### 2024-11-30 paper/paper.qmd
upload paper

---
title: ""
subtitle: ""
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

```{r}
#| include: false
#| warning: false
#| message: false

library(readr)
library(arrow)
library(here)
library(ggplot2)
library(patchwork)

raw_data <- read_delim(here("data/01-raw_data/diamondprice.txt"), delim = "\t")
cleaned_data <- read_parquet(here("data/02-analysis_data/cleaned_diamondprice.parquet"))
train_data <- read_parquet(here("data/02-analysis_data/diamondprice_train_data.parquet"))
test_data <- read_parquet(here("data/02-analysis_data/diamondprice_test_data.parquet"))

model_glm <- readRDS(here("models/glm.rds"))
model_lm <- readRDS(here("models/lm.rds"))

```

# Introduction

# Data {#sec-data}

## Measurement

## Outcome Variable

在appendix里面加入一个关于所有变量的table，然后在这里引用，说明变量类型什么的
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-price
#| fig-cap: "Graphs of Diamond price"

# Graph histogram
# Calculate the mean of diamond prices
mean_price <- mean(cleaned_data$price, na.rm = TRUE)
# Create the histogram with mean line and density curve
histogram_plot <- ggplot(cleaned_data, aes(x = price)) +
  geom_histogram(binwidth = 500, fill = "pink", color = "black", alpha = 0.7) + 
  geom_vline(xintercept = mean_price, linetype = "dashed", color = "salmon") + # Add a dashed vertical line for the mean
  labs(
    x = "Diamond Price",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

# Graph boxplot
boxplot <- ggplot(cleaned_data, aes(x = "", y = price)) +
  geom_boxplot(fill = "lightblue", color = "black", alpha = 0.7, outlier.colour = "salmon") +
  labs(
    x = "",
    y = "Diamond Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- histogram_plot | boxplot
combined_plot

```

## Predictor Variables
在appendix里面加入一个关于所有变量的table，然后在这里引用，说明变量类型什么的
解释每个变量：含义是什么，包括什么值，如何排序
###  Predictor Variables
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-color
#| fig-cap: "Graphs of Predictor Variables: Color"

# Predictor Variables: Color
# Create the histogram with mean line and density curve

color_histogram_plot <- ggplot(cleaned_data, aes(x = color)) +
  geom_bar(binwidth = 3,fill = "lightblue", color = "black", alpha = 0.7) + 
  #scale_x_continuous(
  #  breaks = 1:8, 
  #  labels = c("D", "E", "F", "G", "H", "I", "J", "K"))+
  labs(
    title ="Distribution of Variable: Color",
    x = "Diamond Color",
    y = "Count") +
  theme_minimal() # Use a minimal theme for clean visualization

plot_color <- ggplot(cleaned_data, aes(x = color, y = price,group = 1))+
  geom_point(color = "pink", alpha = 0.7) + 
  geom_smooth(method = "lm", color = "black", se = FALSE) + 
  labs(
    title = "Color vs Price",
    x = "Color",
    y = "Diamond Price"
  ) +
  theme_minimal()

combined_plot <- color_histogram_plot | plot_color
combined_plot

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-carat_size
#| fig-cap: "Graphs of Predictor Variable: Carat Size"

# Graph histogram
# Calculate the mean of diamond prices
mean_size <- mean(cleaned_data$carat_size, na.rm = TRUE)
carat_size_histogram_plot <- ggplot(cleaned_data, aes(x = carat_size)) +
  geom_histogram(fill = "palevioletred", color = "black", alpha = 0.7) +
  geom_vline(xintercept = mean_size, linetype = "dashed", color = "salmon") +
  labs(
    title = "Distribution of Variable: Carat Size",
    x = "Diamond Carat Size",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

plot_carat_size <- ggplot(cleaned_data, aes(x = carat_size, y = price)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_smooth(method = "loess", color = "black", se = FALSE) +
  labs(
    title = "Carat Size vs Price",
    x = "Carat Size",
    y = "Diamond Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- carat_size_histogram_plot | plot_carat_size
combined_plot

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-clarity
#| fig-cap: "Graphs of Predictor Variable: Clarity"

# Graph histogram
# Create the histogram with mean line
clarity_histogram_plot <- ggplot(cleaned_data, aes(x = clarity)) +
  geom_bar(bins = 20, fill = "lightblue", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Variable: Clarity",
    x = "Diamond Clarity",
    y = "Count"
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price, group=1)) +
  geom_point(color = "pink", alpha = 0.7) +
  geom_smooth(method = "loess", color = "black", se = FALSE) +
  labs(
    title = "Clarity vs Price",
    x = "Clarity",
    y = "Diamond Price"
  ) +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Combine 2 plots
combined_plot <- clarity_histogram_plot | plot_clarity
combined_plot

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-cut
#| fig-cap: "Graphs of Predictor Variable: Cut"

# Graph histogram
# Create the histogram with mean line
clarity_histogram_plot <- ggplot(cleaned_data, aes(x = cut)) +
  geom_bar(bins = 20, fill = "palevioletred", color = "black", alpha = 0.7)+
  labs(
    title = "Distribution of Variable: Cut",
    x = "Diamond Cut",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price,group=1)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_smooth(method = "loess", color = "black", se = FALSE) +
  labs(
    title = "Cut vs Price",
    x = "Cut",
    y = "Diamond Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- clarity_histogram_plot | plot_cut
combined_plot

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-correlation
#| fig-cap: "Correlation"

#mosaic plot
library(vcd)
table_data <- xtabs(~ cut + clarity + color, data = cleaned_data)

highlighting_colors <- grDevices::rainbow(8, alpha = 0.5)  # alpha 
options(repr.plot.width = 12, repr.plot.height = 12)  # 宽度和高度可根据需要调整

mosaic(~ cut + clarity + color, data = table_data,
       highlighting = "color",                      # 设置高亮变量为 color
       highlighting_fill = highlighting_colors,    # 使用生成的浅色彩虹
       direction = c("h", "v", "h"), # 控制变量的排列方向
       main = "Relationship Between Cut, Clarity, and Color")

```

## Data Cleaning {#sec-datacleaning}

### Data Split

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 
数据分布不均

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-12-01 paper/paper.qmd
update model set-up

@@
 library(patchwork)
+library(ggplot2)
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
-#| label: fig-correlation
-#| fig-cap: "Correlation"
+#| label: fig-correlation_heat
+#| fig-cap: "Correlation: Heat Graph"
 
-#mosaic plot
-library(vcd)
-table_data <- xtabs(~ cut + clarity + color, data = cleaned_data)
+# 按 cut, color, 和 clarity 聚合 carat_size 的均值
+agg_data <- aggregate(carat_size ~ cut + color + clarity, data = cleaned_data, FUN = mean)
 
-highlighting_colors <- grDevices::rainbow(8, alpha = 0.5)  # alpha 
-options(repr.plot.width = 12, repr.plot.height = 12)  # 宽度和高度可根据需要调整
+#agg_data <- aggregate(carat_size ~ cut + color + clarity, data = #cleaned_data, FUN = median)
 
-mosaic(~ cut + clarity + color, data = table_data,
-       highlighting = "color",                      # 设置高亮变量为 color
-       highlighting_fill = highlighting_colors,    # 使用生成的浅色彩虹
-       direction = c("h", "v", "h"), # 控制变量的排列方向
-       main = "Relationship Between Cut, Clarity, and Color")
+# 绘制分面热图
+ggplot(agg_data, aes(x = cut, y = color, fill = carat_size)) +
+  geom_tile(color = "white") +
+  scale_fill_gradient(low = "lightblue", high = "pink") +
+  facet_wrap(~ clarity) + # 按 clarity 分面
+  labs(title = "Heatmap of Carat Size by Cut, Color, and Clarity",
+       x = "Cut", y = "Color", fill = "Mean Carat Size") +
+  theme_minimal()+
+  theme(axis.text.x = element_text(angle = 20, hjust = 1))+
+  theme(axis.text.y = element_text(size = 6))
 
 ```
-
-## Data Cleaning {#sec-datacleaning}
-
-### Data Split
 
@@
 
+## Data preparation
+包括如何处理reponse来符合gamma。详细请见appendix
+
 ## Model set-up
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define \( y_i \) as the price of the \( i \)-th diamond. Predictors include:
 
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+- \( x_{1i} \): The carat size of the diamond (in carats).
+- \( x_{2i} \): The color grade of the diamond (categorical).
+- \( x_{3i} \): The cut grade of the diamond (categorical).
+- \( x_{4i} \): The clarity grade of the diamond (categorical).
+
+**Model Structure**:
+1. **Response Distribution**:  
+   \( y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi) \),  
+   where \( \mu_i \) is the mean price and \( \phi \) is the dispersion parameter.
+
+2. **Link Function**:  
+   \( \log(\mu_i) = \beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il} \).
+
+   - \( \beta_0 \): Intercept term.  
+   - \( \beta_1 \): Effect of carat size.  
+   - \( \beta_{2j}, \beta_{3k}, \beta_{4l} \): Effects of color, cut, and clarity, respectively.
+
+3. **Mean Price**:  
+   \( \mu_i = \exp(\beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}) \).
+
 \end{align}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
+## Model justification
+以及为什么选择gamma，因为data section 里reponse符合分布
 We expect a positive relationship between the size of the wings and time spent aloft. In particular...
@@
 We can use maths by including latex between dollar signs, for instance $\theta$.
+
+## Model Comparision: Generalized Linear Model vs. Linear Model
+
+## Model Evaluation
+See appendix
 
@@
 #| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory models of Diamond Price based on Color, Cut, Clarity and Carat Size"
 #| warning: false
-#| message: false
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+summary(model_glm)
 ```
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
+#| label: fig-prediction_actual
+#| fig-cap: "Actual vs Predicted Values"
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
+test_data$price <- scale(test_data$price, center = TRUE, scale = TRUE)
+test_data$price<-exp(test_data$price)
+test_data$color <- factor(test_data$color)
+test_data$cut <- factor(test_data$cut)
+test_data$clarity <- factor(test_data$clarity)
+
+test_data$predicted_price <- predict(model_glm, newdata = test_data, type = "response")
+
+ggplot(data = test_data, aes(x = 1:nrow(test_data))) +
+  geom_line(aes(y = predicted_price), color = "lightblue", size = 1, linetype = "solid") + 
+  geom_point(aes(y = price), color = "palevioletred", size = 2) + 
+  labs(
+    x = "Index",
+    y = "Price"
+  ) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+
 ```
+
+## Model Formula
+
+## Example of Prediction
 
@@
 If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-数据分布不均
 
@@
 
-## Third discussion point
+## Limitations
+### Data Limitations
+数据分布不均
+### Model Limitations
 
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
+## Further Considerations
 
@@
 
-# Additional data details
+# Additional data details {#sec-data-details}
+
+## Data Summary
+data section
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-cleaned data
+#| tbl-cap: "First 8 rows of Cleaned data"
+#| warning: false
+
+head_cleaned_data <- head(cleaned_data,8)
+knitr::kable(head_cleaned_data, format = "simple", col.names = c('Diamond Price','Carat Size','Color', 'Clarity','Cut'))
+
+```
+
+## Data Cleaning
+data section
+## Data Preparation and Data Split
+Model Section
+
+response variable
+train test to fit the mode
 
 # Model details {#sec-model-details}
+
+## Model Evaluation
 
@@
 
-pp_check(first_model) +
+pp_check(model_glm) +
   theme_classic() +

### 2024-12-01 scripts/06-model_data.R
Delete extra files

@@ -1,79 +1,0 @@
-#### Preamble ####
-# Purpose: Building Multivariable model
-# Author: Yawen Tan
-# Date: 30 November 2024
-# Contact: yawen.tan@mail.utoronto.ca
-# License: MIT
-
-
-#### Workspace setup ####
-library(arrow)
-library(stats)
-
-#### Data Preparation ####
-train_data <- read_parquet("data/02-analysis_data/diamondprice_train_data.parquet")
-test_data <- read_parquet("data/02-analysis_data/diamondprice_test_data.parquet")
-
-train_data$price <- scale(train_data$price, center = TRUE, scale = TRUE)
-train_data$price<-exp(train_data$price)
-train_data$color <- factor(train_data$color)
-train_data$cut <- factor(train_data$cut)
-train_data$clarity <- factor(train_data$clarity)
-
-
-
-#### Fit Models ####
-# GLM
-model_glm <- glm(price ~ carat_size + color + cut+ clarity,
-                 #family = gaussian(link = "identity"),
-                 family = Gamma(link = "log"),
-                 data = train_data)
-summary(model_glm)
-
-# Linear regression
-model_lm <- lm(price ~ carat_size + color + cut + clarity, data = train_data)
-
-
-#### Save Model ####
-saveRDS(model_glm, "models/glm.rds")
-saveRDS(model_lm, "models/lm.rds")
-
-
-#### Test Model ####
-#Prepare test data
-test_data$price <- scale(test_data$price, center = TRUE, scale = TRUE)
-test_data$price<-exp(test_data$price)
-test_data$color <- factor(test_data$color)
-test_data$cut <- factor(test_data$cut)
-test_data$clarity <- factor(test_data$clarity)
-
-# Find predictions based on 2 models
-predictions_glm <- predict(model_glm, newdata = test_data, type = "response")
-predictions_lm <- predict(model_lm, newdata = test_data)
-# Calculate MSE
-mse_glm <- mean((test_data$price - predictions_glm)^2)
-mse_lm <- mean((test_data$price - predictions_lm)^2)
-
-mse_glm
-mse_lm
-
-#Put in Result section
-library(ggplot2)
-
-test_data$predicted_price <- predict(model_glm, newdata = test_data, type = "response")
-
-
-ggplot(data = test_data, aes(x = 1:nrow(test_data))) +
[…]

### 2024-12-01 scripts/06-model_data.R
update model script

@@ -1,0 +1,96 @@
+#### Preamble ####
+# Purpose: Building Multivariable model
+# Author: Yawen Tan
+# Date: 30 November 2024
+# Contact: yawen.tan@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(arrow)
+library(stats)
+
+#### Data Preparation ####
+train_data <- read_parquet("data/02-analysis_data/diamondprice_train_data.parquet")
+test_data <- read_parquet("data/02-analysis_data/diamondprice_test_data.parquet")
+
+train_data$price <- scale(train_data$price, center = TRUE, scale = TRUE)
+train_data$price<-exp(train_data$price)
+train_data$color <- factor(train_data$color)
+train_data$cut <- factor(train_data$cut)
+train_data$clarity <- factor(train_data$clarity)
+
+
+
+#### Fit Models ####
+# GLM
+model_glm <- glm(price ~ carat_size + color + cut+ clarity,
+                 family = Gamma(link = "log"),
+                 data = train_data)
+summary(model_glm)
+
+# Linear regression
+model_lm <- lm(price ~ carat_size + color + cut + clarity, data = train_data)
+
+
+# Bayes regression
+library(rstanarm)
+model_bayes <-
+  stan_glm(
+    formula = price ~ carat_size + color + cut + clarity,
+    data = train_data,
+    family = Gamma(link = "log"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 141
+  )
+summary(model_bayes)
+
+
+#### Save Model ####
+saveRDS(model_glm, "models/glm.rds")
+saveRDS(model_lm, "models/lm.rds")
+
+
+#### Test Model ####
+#Prepare test data
+test_data$price <- scale(test_data$price, center = TRUE, scale = TRUE)
+test_data$price<-exp(test_data$price)
+test_data$color <- factor(test_data$color)
+test_data$cut <- factor(test_data$cut)
+test_data$clarity <- factor(test_data$clarity)
+
+# Find predictions based on 2 models
+predictions_glm <- predict(model_glm, newdata = test_data, type = "response")
+predictions_lm <- predict(model_lm, newdata = test_data)
[…]

### 2024-12-01 scripts/00-simulate_data.R
update simulated_data

@@ -9,43 +9,28 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
-set.seed(853)
+library(readr)
+library(arrow)
+set.seed(141)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+# Dataset size
+n <- 141
 
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
+# Generate simulated data
+simulated_data <- data.frame(
+  price = sample(1000:10000, n, replace = TRUE), # Price range: 1000-10000 as integers
+  color = sample(c('D', 'E', 'F', 'G', 'H', 'I', 'J', 'K'), n, replace = TRUE), # Color categories
+  cut = sample(c('Ideal', 'Good', 'Very Good', 'Excellent'), n, replace = TRUE), # Cut categories
+  clarity = sample(c('IF', 'VVS1', 'VVS2', 'VS1', 'VS2', 'SI1', 'SI2'), n, replace = TRUE), # Clarity categories
+  carat_size = runif(n, min = 0.2, max = 5.0) # Carat size range: 0.2-5.0
 )
 
 
 #### Save data ####
-write_csv(analysis_data, "data/00-simulated_data/simulated_data.csv")
+write_csv(simulated_data, "data/00-simulated_data/simulated_diamondprice.csv")
+write_parquet(simulated_data, "data/00-simulated_data/simulated_diamondprice.parquet")
+
+

### 2024-12-01 scripts/01-test_simulated_data.R
update test simulated data file

@@ -14,10 +14,11 @@
 #### Workspace setup ####
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+
+simulated_data <- read_csv("data/00-simulated_data/simulated_diamondprice.csv")
 
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
+if (exists("simulated_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
@@ -26,64 +27,54 @@ if (exists("analysis_data")) {
 
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 141 rows
+if (nrow(simulated_data) == 141) {
+  message("Test Passed: The dataset has 141 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 141 rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Check if the dataset has 5 columns
+if (ncol(simulated_data) == 5) {
+  message("Test Passed: The dataset has 5 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The dataset does not have 5 columns.")
 }
 
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
+
+# Check if the 'color' column contains only valid diamond color names
+valid_color <- c('D','E','F','G','H','I','J','K')
+
+if (all(simulated_data$color %in% valid_color)) {
+  message("Test Passed: The 'color' column contains only valid diamond color names.")
 } else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
+  stop("Test Failed: The 'color' column contains invalid color names.")
 }
 
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
-                  "Australian Capital Territory")
 
-if (all(analysis_data$state %in% valid_states)) {
[…]

### 2024-12-01 scripts/01-test_simulated_data.R
add comments in test simulated data file

@@ -1,15 +1,12 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-#electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated data
+# Author: Yawen Tan
+# Date: 30 November 2024
+# Contact: yawen.tan@utoronto.ca
 # License: MIT
 # Pre-requisites: 
 # - The `tidyverse` package must be installed and loaded
 # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-01 paper/paper.qmd
update data section
update graphs in paper.qmd

@@
 histogram_plot <- ggplot(cleaned_data, aes(x = price)) +
-  geom_histogram(binwidth = 500, fill = "pink", color = "black", alpha = 0.7) + 
+  geom_histogram(binwidth = 500, fill = "lightblue", color = "black", alpha = 0.7) + 
   geom_vline(xintercept = mean_price, linetype = "dashed", color = "salmon") + # Add a dashed vertical line for the mean
@@
 boxplot <- ggplot(cleaned_data, aes(x = "", y = price)) +
-  geom_boxplot(fill = "lightblue", color = "black", alpha = 0.7, outlier.colour = "salmon") +
+  geom_boxplot(fill = "pink", color = "black", alpha = 0.7, outlier.colour = "salmon") +
   labs(
@@
 color_histogram_plot <- ggplot(cleaned_data, aes(x = color)) +
-  geom_bar(binwidth = 3,fill = "lightblue", color = "black", alpha = 0.7) + 
+  geom_bar(binwidth = 3,fill = "pink", color = "black", alpha = 0.7) + 
   #scale_x_continuous(
@@
 
-plot_color <- ggplot(cleaned_data, aes(x = color, y = price,group = 1))+
-  geom_point(color = "pink", alpha = 0.7) + 
-  geom_smooth(method = "lm", color = "black", se = FALSE) + 
+# 绘制小提琴图
+violin_plot_color <- ggplot(cleaned_data, aes(x = color, y = price)) +
+  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) +  # 添加小提琴图
+  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +  # 在小提琴图中叠加箱线图
   labs(
-    title = "Color vs Price",
+    title = "Violin Plot of Price by Color",
     x = "Color",
-    y = "Diamond Price"
+    y = "Price"
   ) +
-  theme_minimal()
+  theme_minimal()  # 使用简洁的主题
 
-combined_plot <- color_histogram_plot | plot_color
+# Combine 2 plots
+combined_plot <- color_histogram_plot | violin_plot_color
 combined_plot
-
 ```
@@
 clarity_histogram_plot <- ggplot(cleaned_data, aes(x = clarity)) +
-  geom_bar(bins = 20, fill = "lightblue", color = "black", alpha = 0.7) +
+  geom_bar(bins = 20, fill = "pink", color = "black", alpha = 0.7) +
   labs(
@@
 
-plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price, group=1)) +
-  geom_point(color = "pink", alpha = 0.7) +
-  geom_smooth(method = "loess", color = "black", se = FALSE) +
+boxplot_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
+  geom_boxplot(fill = "lightblue",outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
   labs(
-    title = "Clarity vs Price",
-    x = "Clarity",
-    y = "Diamond Price"
+    title = "Boxplot of Price by Clarity",
+    x = "Cut",
+    y = "Price"
   ) +
-  theme_minimal()+ 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme_minimal()
 
 # Combine 2 plots
-combined_plot <- clarity_histogram_plot | plot_clarity
+combined_plot <- clarity_histogram_plot | boxplot_plot_clarity
 combined_plot
@@
 # Create the histogram with mean line
-clarity_histogram_plot <- ggplot(cleaned_data, aes(x = cut)) +
+cut_histogram_plot <- ggplot(cleaned_data, aes(x = cut)) +
   geom_bar(bins = 20, fill = "palevioletred", color = "black", alpha = 0.7)+
@@
 
-plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price,group=1)) +
-  geom_point(color = "lightblue", alpha = 0.7) +
-  geom_smooth(method = "loess", color = "black", se = FALSE) +
+violin_plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price)) +
+  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
+  geom_boxplot(width = 0.2, outlier.cut = "salmon", outlier.shape = 8, alpha = 0.7) +
   labs(
-    title = "Cut vs Price",
+    title = "Violin Plot of Price by Cut",
     x = "Cut",
-    y = "Diamond Price"
+    y = "Price"
   ) +
@@
 # Combine 2 plots
-combined_plot <- clarity_histogram_plot | plot_cut
+combined_plot <- cut_histogram_plot | violin_plot_cut
 combined_plot
@@
 ```
+Variable type
 

### 2024-12-01 paper/paper.qmd
change box-plot to violin-plot for better visualization

@@
 
-boxplot_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
-  geom_boxplot(fill = "lightblue",outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
+violin_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
+  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
+  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
   labs(
-    title = "Boxplot of Price by Clarity",
-    x = "Cut",
+    title = "Violin Plot of Price by Clarity",
+    x = "Clarity",
     y = "Price"
@@
 # Combine 2 plots
-combined_plot <- clarity_histogram_plot | boxplot_plot_clarity
+combined_plot <- clarity_histogram_plot | violin_plot_clarity
 combined_plot
@@
   geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
-  geom_boxplot(width = 0.2, outlier.cut = "salmon", outlier.shape = 8, alpha = 0.7) +
+  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
   labs(
@@
   theme(axis.text.y = element_text(size = 6))
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
+#| label: fig-correlation_heat
+#| fig-cap: "Correlation: Heat Graph"
 

### 2024-12-02 paper/paper.qmd
add correlation graphs

@@
 number-sections: true
-bibliography: references.bib
+bibliography: 
+  - references.bib
 toc: true
@@
 ## Measurement 
+钻石颜色等数据是如何得出的
+然后提到数据集是如何得出的
+
+## Data Overview
+The data set has 2690 data and 5 variables.
+Variables include response variable diamond price, predictor variables Diamond Color, Diamond Carat Size, Diamond Clarity, Diamond Cut.@tbl-data summarizes the range, variable type and examples of each variable.
+更详细的请见:
+
+We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-data
+#| tbl-cap: "Summary of Diamond Dataset"
+#| warning: false
+
+# Create a data frame summarizing the variables
+summary_table <- data.frame(
+  Attribute = c(
+    "Diamond Price (USD)", 
+    "Diamond Color", 
+    "Diamond Carat Size", 
+    "Diamond Clarity", 
+    "Diamond Cut"
+  ),
+  Range_or_Levels = c(
+    "1000 to 10,000 (USD)", 
+    "D to K (D: Worest, K: Best)", 
+    "0.30 to 2.02", 
+    "SI2, SI1, VS2, VS1, VVS2, VVS1, IF (Low to High)", 
+    "Ideal, Good, Very Good, Excellent (Worst to Best)"
+  ),
+  Data_Type = c(
+    "Numeric", 
+    "Categorical", 
+    "Numeric", 
+    "Categorical", 
+    "Categorical"
+  ),
+  Example = c(
+    "5000", 
+    "G", 
+    "0.8", 
+    "VS1", 
+    "Very Good"
+  )
+)
+
+# Display the table using knitr::kable
+knitr::kable(
+  summary_table, 
+  col.names = c("Attribute", "Range or Levels", "Data Type", "Example")
+)
+
+```
 
@@
 
-在appendix里面加入一个关于所有变量的table，然后在这里引用，说明变量类型什么的
+The diamond price is a continuous numerical variable, ranging from close to 1000 USD to 10,000 USD.
+Through the histogram of @fig-price, we can find that the price of diamonds has obvious right skewness, and with the increase of price, the number of diamonds decreases gradually.
+In addition, combining the histogram and box chart in @fig-price, we can find that there is no obvious abnormal value of diamond prices.
+Most diamond prices are concentrated in the range of 2,500 USD to 5,000 USD, with an average price of about 4,000 USD and a median of 3,500 USD, indicating that a few high-priced diamonds have raised the overall average.
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
@@
   labs(
-    x = "Diamond Price",
+    x = "Diamond Price(USD)",
     y = "Count"
@@
     x = "",
-    y = "Diamond Price"
+    y = "Diamond Price (USD)"
   ) +
@@
 解释每个变量：含义是什么，包括什么值，如何排序
-###  Predictor Variables
+
+### Color
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
@@
     title = "Violin Plot of Price by Color",
-    x = "Color",
-    y = "Price"
+    x = "Diamond Color",
+    y = "Diamond Price (USD)"
   ) +
@@
 ```
+
+### Carat Size
 
@@
     x = "Carat Size",
-    y = "Diamond Price"
+    y = "Diamond Price (USD)"
   ) +
@@
 ```
+
+### Clarity
 
@@
     x = "Clarity",
-    y = "Price"
+    y = "Diamond Price(USD)"
   ) +
@@
 ```
+
+### Cut
 
@@
     title = "Violin Plot of Price by Cut",
-    x = "Cut",
-    y = "Price"
+    x = "Diamond Cut",
+    y = "Diamond Price (USD)"
   ) +
@@
 
-# 按 cut, color, 和 clarity 聚合 carat_size 的均值
-agg_data <- aggregate(carat_size ~ cut + color + clarity, data = cleaned_data, FUN = mean)
+# 加载必要的库
+library(ggcorrplot)
+library(dplyr)
 
-#agg_data <- aggregate(carat_size ~ cut + color + clarity, data = #cleaned_data, FUN = median)
+# Step 1: 创建一个包含独热编码的新的数据集
+correlated_data <- cleaned_data %>%
+  mutate(
+    color = factor(color, levels = c("D", "E", "F", "G", "H", "I", "J", "K")),
+    clarity = factor(clarity, levels = c("SI2", "SI1", "VS2", "VS1", "VVS2", "VVS1", "IF")),
+    cut = factor(cut, levels = c("Ideal", "Good", "Very Good", "Excellent"))
+  )
 
-# 绘制分面热图
-ggplot(agg_data, aes(x = cut, y = color, fill = carat_size)) +
-  geom_tile(color = "white") +
-  scale_fill_gradient(low = "lightblue", high = "pink") +
-  facet_wrap(~ clarity) + # 按 clarity 分面
-  labs(title = "Heatmap of Carat Size by Cut, Color, and Clarity",
-       x = "Cut", y = "Color", fill = "Mean Carat Size") +
-  theme_minimal()+
-  theme(axis.text.x = element_text(angle = 20, hjust = 1))+
-  theme(axis.text.y = element_text(size = 6))
+# 使用 model.matrix 进行独热编码
 
-```
+options(contrasts = c("contr.treatment", "contr.poly")) # 默认对比方法
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
-#| label: fig-correlation_heat
-#| fig-cap: "Correlation: Heat Graph"
+# 强制生成所有列
+one_hot_encoded <- cbind(
+  correlated_data %>% select(price, carat_size), # 数值变量
+  model.matrix(~ color + clarity + cut - 1, data = correlated_data, 
+               contrasts.arg = list(
+                 color = contrasts(correlated_data$color, contrasts = FALSE),
+                 clarity = contrasts(correlated_data$clarity, contrasts = FALSE),
+                 cut = contrasts(correlated_data$cut, contrasts = FALSE)
+               ))
+)
+
+# 检查列名
+colnames(one_hot_encoded)
+
+# 检查独热编码后的列名
+colnames(one_hot_encoded)
+
+# Step 2: 计算相关矩阵
+cor_matrix <- cor(one_hot_encoded, use = "complete.obs")
+
+# Step 3: 自定义列和行的顺序
+custom_order <- c(
+  "price", 
+  paste0("color", c("D", "E", "F", "G", "H", "I", "J", "K")), # Color levels
+  "carat_size", 
+  paste0("clarity", c("SI2", "SI1", "VS2", "VS1", "VVS2", "VVS1", "IF")), # Clarity levels
+  paste0("cut", c("Ideal", "Good", "Very Good", "Excellent")) # Cut levels
+)
+
+# 确保 custom_order 中的变量名存在于 cor_matrix 中
+valid_order <- intersect(custom_order, rownames(cor_matrix))
+
+# 重新排序矩阵的行和列
+cor_matrix <- cor_matrix[valid_order, valid_order]
+
+# Step 4: 绘制相关矩阵热图
+ggcorrplot(
+  cor_matrix, 
+  lab = FALSE,                 # 不显示相关系数的数值
+  hc.order = FALSE,            # 禁用层次聚类，保持指定顺序
+  type = "lower",              # 显示下三角
+  lab_size = 3,                # 数值字体大小
+  colors = c("lightblue", "white", "palevioletred"), # 热图颜色
+  tl.cex = 8                   # 标签字体大小
+)
+
+# 检查 color 的实际水平
+table(correlated_data$color)
+
+# 检查 clarity 的实际水平
+table(correlated_data$clarity)
+
+# 检查 cut 的实际水平
+table(correlated_data$cut)
 
@@
 # Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 # Results
-
-Our results are summarized in @tbl-modelresults.
 
@@
 data section
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-cleaned data
-#| tbl-cap: "First 8 rows of Cleaned data"
-#| warning: false
 
-head_cleaned_data <- head(cleaned_data,8)
-knitr::kable(head_cleaned_data, format = "simple", col.names = c('Diamond Price','Carat Size','Color', 'Clarity','Cut'))
-
-```
 Variable type
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
 ```{r}
@@
 
-pp_check(model_glm) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
 
@@
 
-plot(first_model, "trace")
+#plot(first_model, "trace")
 
-plot(first_model, "rhat")
+#plot(first_model, "rhat")
 ```

### 2024-12-02 paper/paper.qmd
change the title of graphs

@@
 bibliography: 
-  - references.bib
+  - references .bib
 toc: true
@@
 library(ggplot2)
+library(ggcorrplot)
+library(dplyr)
 
@@
 # Data {#sec-data}
-
-## Measurement 
-钻石颜色等数据是如何得出的
-然后提到数据集是如何得出的
 
@@
 ### Color
+def:
+distribution:
+vs price:
 
@@
 color_histogram_plot <- ggplot(cleaned_data, aes(x = color)) +
-  geom_bar(binwidth = 3,fill = "pink", color = "black", alpha = 0.7) + 
-  #scale_x_continuous(
-  #  breaks = 1:8, 
-  #  labels = c("D", "E", "F", "G", "H", "I", "J", "K"))+
+  geom_bar(fill = "pink", color = "black", alpha = 0.7) + 
   labs(
@@
     y = "Count") +
-  theme_minimal() # Use a minimal theme for clean visualization
+  theme_minimal() +
+  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))
 
@@
   ) +
-  theme_minimal()  # 使用简洁的主题
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))
 
@@
   ) +
-  theme_minimal() # Use a minimal theme for clean visualization
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))
 
@@
   ) +
-  theme_minimal()
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))
 
@@
   theme_minimal() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
+  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))
 
@@
   ) +
-  theme_minimal() # Use a minimal theme for clean visualization
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))
 
@@
 #| fig-cap: "Correlation: Heat Graph"
-
-# 加载必要的库
-library(ggcorrplot)
-library(dplyr)
 
@@
 )
-
-# 检查列名
-colnames(one_hot_encoded)
-
-# 检查独热编码后的列名
-colnames(one_hot_encoded)
 
@@
 
-# 检查 color 的实际水平
-table(correlated_data$color)
+```
 
-# 检查 clarity 的实际水平
-table(correlated_data$clarity)
-
-# 检查 cut 的实际水平
-table(correlated_data$cut)
-
-```
+## Measurement 
+钻石颜色等数据是如何得出的
+然后提到数据集是如何得出的
 
@@
 
-\begin{align} 
-- \( x_{1i} \): The carat size of the diamond (in carats).
-- \( x_{2i} \): The color grade of the diamond (categorical).
-- \( x_{3i} \): The cut grade of the diamond (categorical).
-- \( x_{4i} \): The clarity grade of the diamond (categorical).
+\begin{itemize}
+    \item \( x_{1i} \): The carat size of the diamond (in carats).
+    \item \( x_{2i} \): The color grade of the diamond (categorical).
+    \item \( x_{3i} \): The cut grade of the diamond (categorical).
+    \item \( x_{4i} \): The clarity grade of the diamond (categorical).
+\end{itemize}
 
@@
 1. **Response Distribution**:  
-   \( y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi) \),  
+   \[
+   y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi),
+   \]
    where \( \mu_i \) is the mean price and \( \phi \) is the dispersion parameter.
@@
 2. **Link Function**:  
-   \( \log(\mu_i) = \beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il} \).
-
+   \begin{align}
+   \log(\mu_i) &= \beta_0 + \beta_1 x_{1i} 
+   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \nonumber \\
+   &\quad + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
+   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}.
+   \end{align}
    - \( \beta_0 \): Intercept term.  
@@
 3. **Mean Price**:  
-   \( \mu_i = \exp(\beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}) \).
-
+   \begin{align}
+   \mu_i &= \exp\left(\beta_0 + \beta_1 x_{1i} 
+   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \right. \nonumber \\
+   &\quad \left.+ \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
+   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}\right).
    \end{align}

### 2024-12-02 paper/paper.qmd
update data section

@@
 library(dplyr)
+library(knitr)
 
@@
 
+钻石质量的 4C标准，即评判钻石的通用标准：颜色、切割、净度和克拉重量。
+
 # Data {#sec-data}
 
-## Data Overview
+## Overview {#sec-overview}
+
 The data set has 2690 data and 5 variables.
-Variables include response variable diamond price, predictor variables Diamond Color, Diamond Carat Size, Diamond Clarity, Diamond Cut.@tbl-data summarizes the range, variable type and examples of each variable.
-更详细的请见:
+Variables include response variable diamond price, predictor variables Diamond Color, Diamond Carat Size, Diamond Clarity, Diamond Cut.
+@tbl-dataset summarizes the range, variable type and examples of each variable.
+The detailed description of each variables will be presented in outcome variable and predictor variables section.
 
 We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+
+## Measurement {#sec-measurement}
+钻石颜色等数据是如何得出的
+然后提到数据集是如何得出的
 
@@
 #| eval: true
-#| label: tbl-data
+#| label: tbl-dataset
 #| tbl-cap: "Summary of Diamond Dataset"
@@
     "1000 to 10,000 (USD)", 
-    "D to K (D: Worest, K: Best)", 
+    "D to K (D: Best, K: Worst)", 
     "0.30 to 2.02", 
     "SI2, SI1, VS2, VS1, VVS2, VVS1, IF (Low to High)", 
-    "Ideal, Good, Very Good, Excellent (Worst to Best)"
+    "Good, Very Good, Excellent, Ideal (Worst to Best)"
   ),
@@
 
-## Outcome Variable
+## Outcome Variable {#sec-outcomevar}
 
@@
 #| fig-cap: "Graphs of Diamond price"
+#| warning: false
 
@@
 
-## Predictor Variables
-在appendix里面加入一个关于所有变量的table，然后在这里引用，说明变量类型什么的
-解释每个变量：含义是什么，包括什么值，如何排序
+## Predictor Variables {#sec-predictorvar}
 
-### Color
-def:
-distribution:
-vs price:
+### Color{#sec-color}
+
+The diamond color, a categorical variable, represents the degree of colorlessness of a diamond.
+It has seven categories in the dataset, ranging from the letter D (completely colorless) to the letter K (faint yellow or brown tint), based on the GIA (Gemological Institute of America) grading system.
+-   D is the highest grade, completely colorless and the rarest and most expensive color in diamonds. 
+-   E and F grades are almost colorless, and extremely weak tones can only be detected under professional instruments. 
+-   G and H grades still look almost colorless, and only when compared with higher grades in bright light can a slight yellow or brown tone be observed. 
+-   I and J began to show slightly yellow tint visible, especially in larger diamonds. 
+-   K shows obvious yellow tone or brown tone.
+
+The barplot on the left of @fig-color shows the distribution of diamond color from D to K.
+The barplot shows that the number of diamonds with color grades E and F is the largest, indicating that these nearly colorless diamonds are more popular in the market, probably because they have high quality and cost performance.
+In contrast, the number of completely colorless D-class diamonds and K-class diamonds with slight yellow is small, which may be due to their rarity and color deviation, respectively, resulting in low demand.
+This picture directly reflects the supply of diamonds of different color grades in the market and their potential demand trends.
+The violin chart on the right of @fig-color shows the distribution of diamond prices in different color grades.
+The violio chart shows that the prices of diamonds with color grades D to F are generally higher, especially those with color grades D and E, which shows a wider price distribution range, indicating that the prices of high-end diamonds with these color grades can increase significantly.
+In contrast, the price distribution of diamonds with color grades I to K is more concentrated and the overall price is lower, reflecting that the price fluctuation of diamonds close to yellow is less in the market.
+In addition, there are significant outliers in top colors such as D and E, which may be due to the unusually high price of diamonds with large carats or other high-quality characteristics.
+This figure clearly reveals the influence of color grade on price and its market value distribution characteristics.
 
@@
 
-### Carat Size
+### Carat Size{#sec-caratsize}
+
+The diamond carat size, a continuous numerical variable representing the weight of the diamond, ranges from approximately 0.30 to 2.02 carats in the dataset.
+One carat is equivalent to 200 milligrams, making it a key factor in determining the diamond's size and price.
+The histogram on the left of @fig-carat_size shows the distribution of the Carat Size of diamonds.
+On the whole, it presents a right-skewed distribution, indicating that the number of small carats (such as 0.5 to 1.0 carats) is the largest in the market, while the number of larger carats is gradually decreasing.
+The red dotted line in the figure indicates the average carat size, and it can be seen that the carat size of most diamonds is concentrated on the left side of the average, which further reflects the dominant position of small carat diamonds in the market.
+This reflects that consumers have higher demand for small carats, while large carats are scarce because of their rarity and high price.
+The scatter chart on the right of @fig-carat_size shows the relationship between the carat size of diamonds and the price.
+It can be clearly seen that the price rises rapidly with the increase of carat size, showing a nonlinear growth trend.
+Especially in the range of close to 1.0 carats and larger carats, the price increase is more significant.
+This shows that the carat size has an important influence on the diamond price, but when the Dancla size exceeds a certain value (such as 1.5 carats), the price growth rate tends to be flat.
+In addition, the fitted black curve further clearly shows this nonlinear relationship, indicating that the marginal effect of carat size on price decreases.
 
@@
 
-### Clarity
+### Clarity{#sec-clarity}
+
+The diamond clarity, representing the number, size, location, and visibility of internal inclusions and external blemishes in a diamond, is a categorical variable with seven categories in the dataset: IF, VVS1, VVS2, VS1, VS2, SI1, and SI2.
+According to the GIA grading system, diamond clarity decreases progressively from IF (Internally Flawless) to SI (Slightly Included).
+
+-   Internally Flawless (IF) diamonds are characterized by having no visible inclusions under 10x magnification, which is nearly flawless.
+The only possible imperfections might be extremely fine surface blemishes, such as polishing marks, which can typically be removed with re-polishing.
+-   Very Very Slightly Included (VVS) diamonds are divided into two subgrades: VVS1 and VVS2.
+VVS1 diamonds have extremely small inclusions that are barely detectable under 10x magnification, typically located at the pavilion (the bottom part of the diamond).
+VVS2 diamonds may have slightly more inclusions, such as tiny feather-like marks or minute blemishes, but these still require professional tools to identify.
+-   Very Slightly Included (VS) diamonds are classified into two subgrades: VS1 and VS2.
+VS1 diamonds have very small inclusions that are detectable under 10x magnification but careful observation to identify.
+VS2 diamonds contain relatively minor inclusions such as small feather-like marks or pinpoints, have more noticeable imperfections under magnification, but these imperfections have minimal impact on the diamond's overall appearance.
+-   Slightly Included (SI) diamonds are categorized into two subgrades: SI1 and SI2.
+SI1 diamonds have inclusions that are more noticeable under 10x magnification and can be easily detected using professional tools.
+SI2 diamonds contain more inclusions, which are larger or more prominent, but these imperfections are typically not visible to the naked eye in most conditions.
+
+The barplot on the left of @fig-clarity shows the distribution of diamond Clarity.
+It shows that the number of diamonds with clarity grades SI1 and SI2 is the largest, indicating that these grades of diamonds are the most widely available in the market, probably because they have higher cost performance and greater market demand.
+In contrast, the number of diamonds with clarity grade of IF(Internally Flawless) is the least, which reflects the rarity of completely flawless diamonds.
+This shows that diamonds with lower definition grades (such as SI1 and SI2) are the main ones in the market, while high definition diamonds are scarce.
+The violin chart on the right of @fig-clarity shows the distribution of diamond prices at different clarity levels.
+With the improvement of clarity, the price rises significantly, especially for diamonds with high definition such as IF and VVS1.
+The price distribution is wider and there are obvious outliers, which may be caused by the carat size or other quality characteristics of these diamonds.
+On the other hand, the price distribution of grades with low definition (such as SI1 and SI2) is relatively concentrated, and the median is obviously lower than that of high-grade diamonds, but their price range shows their stable demand and high cost performance in the market.
 
@@
 
-### Cut
+### Cut{#sec-cut}
+
+The diamond Cut measures the quality of diamond cutting, which determines how a diamond reflects light, thus affecting its brightness, fire and scintillation.The diamond cut in the data set is a categorical variable with four categories: Excellent, Very Good, Good, and Ideal.
+According to the grading systems of GIA and AGS, cut quality decreases from Ideal to Good.
+
+-   The Ideal cut with nearly all incoming light reflecting through the diamond's top to maximize brilliance and sparkle.
+It features balanced and prominent fire and scintillation, with precisely cut crown and pavilion angles to achieve optimal light refraction.
+Proportional standards, such as table percentage and pavilion depth percentage, meet ideal criteria.
+The facets are perfectly aligned with no visible deviations, and the surface is finely polished, free from any scratches or blemishes.
+-   Excellent cut diamonds reflect nearly all light through the top, showcasing maximum brilliance and fire.
+As the high cut grade, they exhibit optimal optical performance and exceptional visual appeal.
+-   Very Good cut diamonds reflect most of the light through the top, though a small amount may escape from the sides or bottom and their brilliance and fire are slightly less than those of Excellent cut diamonds.
+-   Good cut diamonds exhibit noticeably reduced light refraction, with some light escaping from the sides or bottom and their brilliance and fire are not as strong as higher-grade cuts.
+
+The barplot on the left of @fig-cut shows the distribution of diamonds with different cutting grades.
+It indicates that the number of diamonds with Excellent and Very Good grades is obviously more, indicating that most diamonds on the market are concentrated in these high-cut grades, which may be because they have better visual effects and higher market demand.
+In contrast, the number of Good and Ideal diamonds is small, especially the rarity of Ideal cutting may reflect strict cutting ratio requirements and high quality standards.
+The violin chart on the right of @fig-cut shows the price distribution of diamonds with different cutting grades.
+It shows the price range of each cutting grade is very close to the median, which shows that the cutting grade has little direct influence on the price.
+However, Ideal and Excellent diamonds are more obviously distributed in the high-end price range, which may be because these two grades of diamonds are usually combined with other high-quality characteristics, such as high carat number or clarity.
+At the same time, the overall price range is relatively large, indicating that other factors (such as carats, colors, etc.) may play a more important role in determining the price.
 
@@
 
+## Analysis of Correlation{#sec-correlation}
+
+@fig-correlation_heat shows several key insights about the relationships between diamond attributes and price.
+Carat size shows a strong positive correlation with price, indicating that it is one of the primary factors influencing diamond value—larger diamonds tend to be more expensive.
+In contrast, cut (e.g., cutExcellent, cutVery Good) demonstrates a weaker correlation with price, suggesting that cut grade alone has a limited direct impact on diamond cost but may work in conjunction with other factors such as carat size or color.
+Similarly, color (e.g., colorD to colorK) shows a weak correlation with price, with diamonds closer to colorless (e.g., colorD and colorE) potentially commanding higher prices, but the overall effect is minimal.
+Clarity (e.g., clarityIF to claritySI2) also exhibit a modest relationship with price, reflecting their role as a contributing but less dominant factor in determining diamond value.
+Overall, carat size emerges as the most influential attribute, while other variables like cut, color, and clarity play supporting roles.
+@fig-correlation_heat also presents the relationships between the predictor variables, showing that the correlations among them are generally weak.
+For example, attributes like cut quality, clarity, color, and carat size do not exhibit strong intercorrelations, as most of the corresponding cells are closer to white or light blue.
+This suggests that the predictor variables are relatively independent, reducing the risk of multicollinearity in the analysis.
+The weak correlations among these variables ensure that each contributes uniquely to the model, providing a robust foundation for predicting diamond price.
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
@@
 
-# Step 1: 创建一个包含独热编码的新的数据集
 correlated_data <- cleaned_data %>%
@@
 
-# 使用 model.matrix 进行独热编码
+options(contrasts = c("contr.treatment", "contr.poly"))
 
-options(contrasts = c("contr.treatment", "contr.poly")) # 默认对比方法
-
-# 强制生成所有列
 one_hot_encoded <- cbind(
@@
 
-# Step 2: 计算相关矩阵
 cor_matrix <- cor(one_hot_encoded, use = "complete.obs")
 
-# Step 3: 自定义列和行的顺序
 custom_order <- c(
@@
 
-# 确保 custom_order 中的变量名存在于 cor_matrix 中
 valid_order <- intersect(custom_order, rownames(cor_matrix))
 
-# 重新排序矩阵的行和列
 cor_matrix <- cor_matrix[valid_order, valid_order]
 
-# Step 4: 绘制相关矩阵热图
 ggcorrplot(
   cor_matrix, 
-  lab = FALSE,                 # 不显示相关系数的数值
-  hc.order = FALSE,            # 禁用层次聚类，保持指定顺序
-  type = "lower",              # 显示下三角
-  lab_size = 3,                # 数值字体大小
-  colors = c("lightblue", "white", "palevioletred"), # 热图颜色
-  tl.cex = 8                   # 标签字体大小
+  lab = FALSE,             
+  hc.order = FALSE,        
+  type = "lower",       
+  lab_size = 3,               
+  colors = c("lightblue", "white", "palevioletred"),
+  tl.cex = 8                  
 )
@@
 
-## Measurement 
-钻石颜色等数据是如何得出的
-然后提到数据集是如何得出的
-
-# Model
+# Model{#sec-model}
 
@@
 
-## Model set-up
+## Model set-up{#sec-modelsetup}
 
@@
 
-## Model justification
-以及为什么选择gamma，因为data section 里reponse符合分布
+## Model justification{#sec-justification}
+为什么选择glm，以及为什么选择gamma，因为data section 里reponse符合分布
 We expect a positive relationship between the size of the wings and time spent aloft. In particular...
@@
 
-## Model Comparision: Generalized Linear Model vs. Linear Model
+## Model Comparision: Generalized Linear Model vs. Linear Model {#sec-compare}
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelcompare
+#| tbl-cap: "Model Reulst: Prediction of Diamond Price based on Color, Cut, Clarity and Carat Size"
+#| warning: false
+aic_value <- AIC(model_glm)
+bic_value <- BIC(model_glm)
 
-## Model Evaluation
+cat("AIC:", aic_value, "\n")
+cat("BIC:", bic_value, "\n")
+```
+
+## Model Evaluation{#sec-evaluation}
 See appendix
 
-# Results
+# Results{#sec-result}
+## Model Result{#sec-modelresult}
 
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of Diamond Price based on Color, Cut, Clarity and Carat Size"
+#| tbl-cap: "Model Reulst: Prediction of Diamond Price based on Color, Cut, Clarity and Carat Size"
 #| warning: false
 
+# 获取 model_glm 的系数摘要
+model_summary <- summary(model_glm)$coefficients
+
+# 将摘要转换为数据框，便于 knitr::kable 格式化
+model_summary_df <- as.data.frame(model_summary)
 summary(model_glm)
+# 使用 knitr::kable 输出表格
+knitr::kable(
+  model_summary_df,
+  digits = 3,  # 设置小数点后保留 3 位
+  format = "pipe"  # 输出格式，可选 "html", "latex", "pipe" 等
+)
 ```
+
+## Predictions vs Actual Value{#sec-predictions}
 
@@
 
-## Model Formula
+## Example of Prediction{#sec-example}
 
-## Example of Prediction
-
-# Discussion
+# Discussion{#sec-discussion}
 
@@
 
-## Second discussion point
+## Limitations{#sec-limitation}
+### Data Limitations{#sec-datalimit}
+数据分布不均
+### Model Limitations{#sec-modellimit}
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Limitations
-### Data Limitations
-数据分布不均
-### Model Limitations
-
-## Further Considerations
+## Further Considerations{#sec-further}
 
@@
 
-# Additional data details {#sec-data-details}
+# Additional data details {#sec-addtionaldata}
 
-## Data Summary
+## Data Cleaning{#sec-dataclean}
 data section
-
-Variable type
-
-## Data Cleaning
-data section
-## Data Preparation and Data Split
+## Data Preparation and Data Split{#sec-dataprepare}
 Model Section
@@
 
-# Model details {#sec-model-details}
+# Additional Model details {#sec-model-details}
 
-## Model Evaluation
+## Evaluation Metrics and Diagnostic Table{#sec-evaluation}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
+#| label: fig-evaluation
+#| fig-cap: "Actual vs Predicted Values"
 
-## Posterior predictive check
+# 加载必要的库
+library(knitr)
+
+# 假设 `model_glm` 是基于 `train_data` 构建的模型
+# 假设 `test_data` 是用于测试的独立数据集
+
+# 1. 使用 test_data 计算 MSE 和 MAE
+predicted_test <- predict(model_glm, newdata = test_data, type = "response")
+actual_test <- test_data$price  # 假设价格列为 'price'
+
+# 计算 MSE 和 MAE
+mse_test <- mean((predicted_test - actual_test)^2)
+mae_test <- mean(abs(predicted_test - actual_test))
+
+# 2. 基于 train_data 的 R² 和 Adjusted R²
+# 计算总平方和和回归平方和
+actual_train <- train_data$price
+predicted_train <- predict(model_glm, newdata = train_data, type = "response")
+
+ss_total <- sum((actual_train - mean(actual_train))^2)
+ss_residual <- sum((actual_train - predicted_train)^2)
+
+# 计算 R² 和 Adjusted R²
+r_squared <- 1 - (ss_residual / ss_total)
+n <- nrow(train_data)
+p <- length(coef(model_glm)) - 1  # 模型中的预测变量数量
+adjusted_r_squared <- 1 - ((1 - r_squared) * (n - 1) / (n - p - 1))
+
+# 3. 计算过度离散性
+dispersion_ratio <- deviance(model_glm) / df.residual(model_glm)
+
+# 4. 将结果格式化为表格
+
+# 结果 1：基于测试集的 MSE 和 MAE
+test_results <- data.frame(
+  Metric = c("MSE (Test)", "MAE (Test)"),
+  Value = c(mse_test, mae_test)
+)
+
+# 结果 3：过度离散性: summary(model)里面有
+dispersion_result <- data.frame(
+  Metric = "Dispersion Ratio",
+  Value = dispersion_ratio
+)
+
+# 使用 knitr::kable 将表格输出
+cat("### Test Data Results\n")
+kable(test_results, caption = "Performance Metrics on Test Data", digits = 3)
+
+cat("\n### Dispersion Check\n")
+kable(dispersion_result, caption = "Overdispersion Check", digits = 3)
+
+```
+
+## Feature importance analysis{#sec-importance}
 
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
+#| label: fig-feature_importance
 #| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+#| fig-cap: "Feature importance analysis"
+
+library(broom)
+
+coefficients <- tidy(model_glm)
+ggplot(coefficients, aes(x = reorder(term, estimate), y = estimate)) +
+  geom_bar(stat = "identity", fill = "lightblue") +
+  coord_flip() +
+  labs(title = "Variable Importance", x = "Variables", y = "Estimates") +
+  theme_minimal()
 
@@
 
-## Diagnostics
+## Diagnostics{#sec-diagonsis}
 
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| fig-cap: "Diagonsis"
 
-#plot(first_model, "trace")
+par(mfrow = c(2, 2))  # 生成 2x2 子图布局
+plot(model_glm)
 
-#plot(first_model, "rhat")
 ```
@@
 
-# References
+# References{#sec-refer}

### 2024-12-02 scripts/04-test_analysis_data.R
update test cleaned data

@@ -1,69 +1,86 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the cleaned data
+# Author: Yawen Tan
+# Date: 30 November 2024
+# Contact: yawen.tan@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: 
+# - The `tidyverse` package must be installed and loaded
+# - 03-clean_data.R must have been run
 
 #### Workspace setup ####
 library(tidyverse)
-library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+cleaned_data <- read_parquet(here("data/02-analysis_data/cleaned_diamondprice.parquet"))
+
+
+# Test if the data was successfully loaded
+if (exists("cleaned_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
+# Check if the dataset has 2690 rows
+if (nrow(cleaned_data) == 2690) {
+  message("Test Passed: The dataset has 2690 rows.")
+} else {
+  stop("Test Failed: The dataset does not have 2690 rows.")
+}
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
+# Check if the dataset has 5 columns
+if (ncol(cleaned_data) == 5) {
+  message("Test Passed: The dataset has 5 columns.")
+} else {
+  stop("Test Failed: The dataset does not have 5 columns.")
+}
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
-})
 
-# Test that the 'state' column is character type
-test_that("'state' is character", {
[…]

### 2024-12-02 paper/paper.qmd
update model set-up

@@
 ---
-title: ""
-subtitle: ""
+title: "my title"
+subtitle: "subtitle"
 author: 
@@
 date-format: long
-abstract: ""
+abstract: "4 sentence"
 format: pdf
@@
 
-## Measurement {#sec-measurement}
-钻石颜色等数据是如何得出的
-然后提到数据集是如何得出的
-
 ```{r}
@@
 ```
+## Measurement {#sec-measurement}
 
-## Outcome Variable {#sec-outcomevar}
+@gia_4cs illustrates the measurement of diamond features.
+Color is conducted by comparing the diamond against GIA’s master stones (graded from D to Z) under controlled lighting and background conditions, as light sources significantly affect appearance.
+At least two graders assess each diamond's color, with additional graders involved if discrepancies arise, until a consensus is reached.
+Clarity is performed under 10x magnification in standard observation conditions, where the grader examines internal and external characteristics, documenting inclusions, blemishes, or treatments such as laser drilling or fracture filling.
+Cut utilizes high-precision instruments to measure cutting proportions, angles, symmetry, and polish quality, following international standards set by organizations like GIA or AGS, with grades such as Excellent and Very Good.
+Carat size is determined using highly accurate electronic microbalances, capable of measuring to five decimal places, or one ten-thousandth of a carat, complemented by optical devices to assess the diamond’s proportions, dimensions, and facet angles.
+
+## Outcome Variable: Price {#sec-outcomevar}
 
@@
 
-## Data preparation
-包括如何处理reponse来符合gamma。详细请见appendix
+The goal of our modelling strategy is twofold. Firstly,...
+
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define \( y_i \) as the price of the \( i \)-th diamond. Predictors include:
+Define $y_i$  as the price of the i th diamond. Predictors include:
 
-\begin{itemize}
-    \item \( x_{1i} \): The carat size of the diamond (in carats).
-    \item \( x_{2i} \): The color grade of the diamond (categorical).
-    \item \( x_{3i} \): The cut grade of the diamond (categorical).
-    \item \( x_{4i} \): The clarity grade of the diamond (categorical).
-\end{itemize}
+-   $x_{1i}$: The carat size of the diamond (in carats).
+-   $x_{2i}$: The color grade of the diamond (categorical).
+-   $x_{3i}$: The cut grade of the diamond (categorical).
+-   $x_{4i}$: The clarity grade of the diamond (categorical).
 
-**Model Structure**:
 1. **Response Distribution**: 
-   \[
-   y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi),
-   \]
-   where \( \mu_i \) is the mean price and \( \phi \) is the dispersion parameter.
+   \begin{align}
+   y_i |\mu_i, \phi \sim \text{Gamma}(\mu_i, \phi),
+   \end{align}
+   where $\mu_i$ is the mean price and $\phi$ is the dispersion parameter.
 
 2. **Link Function**:
+
    \begin{align}
-   \log(\mu_i) &= \beta_0 + \beta_1 x_{1i} 
-   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \nonumber \\
-   &\quad + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
-   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}.
+   \log(\mu_i) &= \beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \nonumber \\
+   &\quad + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}.
    \end{align}
-   - \( \beta_0 \): Intercept term.  
-   - \( \beta_1 \): Effect of carat size.  
-   - \( \beta_{2j}, \beta_{3k}, \beta_{4l} \): Effects of color, cut, and clarity, respectively.
+   - $\beta_0$: Intercept term.  
+   - $\beta_1$: Effect of carat size.  
+   - $\beta_{2j}$, $\beta_{3k}$, $\beta_{4l}$: Effects of j color, k cut, and l clarity, where j includes: D,E,F,G,H,I,J,K; k includes: Ideal, Excellent, Very Good, Good; l include IF, VVS1, VVS2, VS1, VS2, SI1, SI2.
 
@@
    \begin{align}
-   \mu_i &= \exp\left(\beta_0 + \beta_1 x_{1i} 
-   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \right. \nonumber \\
-   &\quad \left.+ \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
-   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}\right).
+   \mu_i &= \exp\left(\beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \right. \nonumber \\
+   &\quad \left.+ \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}\right)
    \end{align}
@@
 为什么选择glm，以及为什么选择gamma，因为data section 里reponse符合分布
+
 We expect a positive relationship between the size of the wings and time spent aloft. In particular...
@@
 
-cat("AIC:", aic_value, "\n")
-cat("BIC:", bic_value, "\n")
 ```

### 2024-12-02 scripts/00-simulate_data.R
add pre-requisites for running R file

@@ -4,9 +4,8 @@
 # Date: 30 November 2024
 # Contact: yawen.tan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
+# Pre-requisites: 
+# - The `readr`,`arrow` package must be installed and loaded
 
 #### Workspace setup ####
 library(readr)

### 2024-12-02 scripts/03-clean_data.R

@@ -1,10 +1,12 @@
 #### Preamble ####
 # Purpose: Cleans the raw data
 # Author: Yawen Tan
-# Date: 28 November 2024
+# Date: 01 December 2024
 # Contact: yawen,tan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
+# Pre-requisites: 
+# - The `readr`,`arrow`,`caTools`,`dplyr` package must be installed and loaded
+# - 02-download_data.R must have been run
 
 #### Workspace setup ####
 library(readr)

### 2024-12-02 scripts/06-model_data.R
Add Bayes regression model

@@ -1,14 +1,18 @@
 #### Preamble ####
-# Purpose: Building Multivariable model
+# Purpose: Building Multivariable model: Generalize Linear model, Linear model, Bayes Regression Model
 # Author: Yawen Tan
-# Date: 30 November 2024
+# Date: 01 December 2024
 # Contact: yawen.tan@mail.utoronto.ca
 # License: MIT
+# Pre-requisites: 
+# - The `arrow`,`stats`,`rstanarm` package must be installed and loaded
+# - 03-clean_data.R must have been run
 
 
 #### Workspace setup ####
 library(arrow)
 library(stats)
+library(rstanarm)
 
 #### Data Preparation ####
 train_data <- read_parquet("data/02-analysis_data/diamondprice_train_data.parquet")
@@ -34,7 +38,6 @@ model_lm <- lm(price ~ carat_size + color + cut + clarity, data = train_data)
 
 
 # Bayes regression
-library(rstanarm)
 model_bayes <-
   stan_glm(
     formula = price ~ carat_size + color + cut + clarity,
@@ -45,52 +48,10 @@ model_bayes <-
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 141
   )
-summary(model_bayes)
 
 
 #### Save Model ####
 saveRDS(model_glm, "models/glm.rds")
 saveRDS(model_lm, "models/lm.rds")
-
-
-#### Test Model ####
-#Prepare test data
-test_data$price <- scale(test_data$price, center = TRUE, scale = TRUE)
-test_data$price<-exp(test_data$price)
-test_data$color <- factor(test_data$color)
-test_data$cut <- factor(test_data$cut)
-test_data$clarity <- factor(test_data$clarity)
-
-# Find predictions based on 2 models
-predictions_glm <- predict(model_glm, newdata = test_data, type = "response")
-predictions_lm <- predict(model_lm, newdata = test_data)
-predictions_bayes <- predict(model_bayes, newdata = test_data)
-# Calculate MSE
-mse_glm <- mean((test_data$price - predictions_glm)^2)
-mse_lm <- mean((test_data$price - predictions_lm)^2)
-mse_bayes <- mean((test_data$price - predictions_bayes)^2)
-
-mse_glm
-mse_lm
-mse_bayes
-
-#Put in Result section
-library(ggplot2)
-
[…]

### 2024-12-03 scripts/06-model_data.R
change bayes regression

@@ -43,15 +43,14 @@ model_bayes <-
     formula = price ~ carat_size + color + cut + clarity,
     data = train_data,
     family = Gamma(link = "log"),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 141
+    prior = normal(location = 0, scale = 10, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 10, autoscale = TRUE),
+    prior_aux = exponential(rate = 3, autoscale = TRUE),
   )
 
 
 #### Save Model ####
 saveRDS(model_glm, "models/glm.rds")
 saveRDS(model_lm, "models/lm.rds")
-saveRDS(model_lm, "models/bayes.rds")
+saveRDS(model_bayes, "models/bayes.rds")
 

### 2024-12-03 scripts/06-model_data.R
update model by redefining reference level

@@ -16,14 +16,16 @@ library(rstanarm)
 
 #### Data Preparation ####
 train_data <- read_parquet("data/02-analysis_data/diamondprice_train_data.parquet")
-test_data <- read_parquet("data/02-analysis_data/diamondprice_test_data.parquet")
 
+#Scale and exponent the response variable
 train_data$price <- scale(train_data$price, center = TRUE, scale = TRUE)
 train_data$price<-exp(train_data$price)
-train_data$color <- factor(train_data$color)
-train_data$cut <- factor(train_data$cut)
-train_data$clarity <- factor(train_data$clarity)
 
+# Covert categorical variables into factors
+# Redefine the factor level order so that the first value automatically becomes the reference level
+train_data$color <- factor(train_data$color, levels = c('K','J','I','H','G','F','E','D'))
+train_data$clarity <- factor(train_data$clarity, levels = c('SI2','SI1','VS2','VS1','VVS2','VVS1','IF'))
+train_data$cut <- factor(train_data$cut, levels = c('Good','Very Good','Excellent','Ideal'))
 
 
 #### Fit Models ####
@@ -31,7 +33,7 @@ train_data$clarity <- factor(train_data$clarity)
 model_glm <- glm(price ~ carat_size + color + cut+ clarity,
                  family = Gamma(link = "log"),
                  data = train_data)
-summary(model_glm)
+
 
 # Linear regression
 model_lm <- lm(price ~ carat_size + color + cut + clarity, data = train_data)
@@ -47,7 +49,6 @@ model_bayes <-
     prior_intercept = normal(location = 0, scale = 10, autoscale = TRUE),
     prior_aux = exponential(rate = 3, autoscale = TRUE),
   )
-
 
 #### Save Model ####
 saveRDS(model_glm, "models/glm.rds")

### 2024-12-03 paper/paper.qmd
update data overview
upload second draft

@@
 model_lm <- readRDS(here("models/lm.rds"))
+model_bayes <- readRDS(here("models/bayes.rds"))
 
@@
 @tbl-dataset summarizes the range, variable type and examples of each variable.
-The detailed description of each variables will be presented in outcome variable and predictor variables section.
+The detailed description of each variables will be presented in outcome variable and predictor variables section.To ensure data quality and clarity, all missing values were removed, and column names were standardized for consistency and readability.
+Additionally, key categorical variables, including color, cut, and clarity, were converted into factors to appropriately represent their categorical nature in the analysis.
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+We use the statistical programming language R [@citeR], alongside several key libraries and datasets to analyze and visualize data effectively.
+Our data [@diamonds_data] is sourced from the Data and Story Library, providing detailed attributes of diamonds for multiple regression analysis.
+Following @tellingstories, we consider how storytelling principles can enhance data interpretation and presentation.
+The tidyverse ecosystem [@citetidyverse] underpins our data manipulation and visualization, with dplyr [@citedplyr] for data wrangling and ggplot2 integrated packages to create visualizations.
+The here package [@citehere] simplifies file path management, while knitr [@citeknitr] and patchwork [@patchwork] streamline report generation and composite plotting.
+Bayesian modeling is conducted with rstanarm [@rstanarm], leveraging robust statistical frameworks.
+Additionally, caTools [@caTools] aids in statistical operations such as ROC curve analysis, and ggcorrplot [@ggcorrplot] facilitates correlation visualization.
 
@@
 It has seven categories in the dataset, ranging from the letter D (completely colorless) to the letter K (faint yellow or brown tint), based on the GIA (Gemological Institute of America) grading system.
+
 -   D is the highest grade, completely colorless and the rarest and most expensive color in diamonds. 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modeling strategy is twofold: to assess the contributions of key factors—such as carat size, diamond color, cut, and clarity—to variations in the standardized and transformed diamond price, and to provide accurate predictions of diamond prices based on these features.
+We use generalized linear model (GLM) implemented using the `glm` function in @citeR.
+The GLM model investigates the relationship between standardized, transformed diamond prices and predictors like carat size, color, cut, and clarity, using the Gamma family with a log link function.
+The dataset is divided into training and testing sets, with 70% of the data allocated for model fitting and parameter estimation, and the remaining 30% reserved for evaluating predictive accuracy.Background details, model evalution, diagnostics and model predictions are included in [Appendix -@sec-model-details].
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+## Data Preprocession{#sec-dataprepare}
 
-## Model set-up{#sec-modelsetup}
+Before building the model, the data underwent several preprocessing steps to ensure compatibility and improve model performance.
+The response variable `price` was standardized because its values were significantly larger compared to other continuous numeric variables 'carat_size', which could disproportionately influence the model.
+After scaling, the response variable was transformed using the exponential function to ensure that `price` remained positive, making it more interpretable and suitable for subsequent analysis.Then, categorical variables, including `color`, `clarity`, and `cut`, were explicitly converted into factors to enable proper handling in the GLM model.
+Additionally, the levels of these categorical variables were reordered to define reference levels:
+-   Variable 'color' have reference level 'K'(worst color)
+-   Variable 'clarity' have reference level 'SI2' (worst clarity)
+-   Variable 'cut' have reference level 'Good' (worst cut)
 
-Define $y_i$  as the price of the i th diamond. Predictors include:
+## Model Set-up{#sec-modelsetup}
 
--   $x_{1i}$: The carat size of the diamond (in carats).
--   $x_{2i}$: The color grade of the diamond (categorical).
--   $x_{3i}$: The cut grade of the diamond (categorical).
--   $x_{4i}$: The clarity grade of the diamond (categorical).
+The GLM relies on several key assumptions.
+Firstly, we assume the response variable $y_i$ (diamond prices) is assumed to follow a Gamma distribution with mean $\mu_i$ and dispersion parameter $\phi$.
+Then, we assume there is a linear relationship between the predictors and the logarithm of the mean price $\log(\mu_i)$ in the transformed space.
+The assumptions underlying this GLM model are as follows (1) and (2):
 
-1. **Response Distribution**: 
 \begin{align}
-   y_i |\mu_i, \phi \sim \text{Gamma}(\mu_i, \phi),
+y_i \mid \mu_i, \phi &\sim \text{Gamma}(\mu_i, \phi),
 \end{align}
 where $\mu_i$ is the mean price and $\phi$ is the dispersion parameter.
-
-2. **Link Function**:
 
@@
 \end{align}
-   - $\beta_0$: Intercept term.  
-   - $\beta_1$: Effect of carat size.  
-   - $\beta_{2j}$, $\beta_{3k}$, $\beta_{4l}$: Effects of j color, k cut, and l clarity, where j includes: D,E,F,G,H,I,J,K; k includes: Ideal, Excellent, Very Good, Good; l include IF, VVS1, VVS2, VS1, VS2, SI1, SI2.
 
-3. **Mean Price**:  
+Then, based on these assumptions of GLM, we get the final generalized linear model (3):
+
 \begin{align}
-   \mu_i &= \exp\left(\beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \right. \nonumber \\
-   &\quad \left.+ \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}\right)
+\log(\text{standardized\ and\ exponentiated\ price}) &= \beta_0 + \beta_1 \cdot \text{carat\_size} \nonumber \\
+&\quad + \sum_{i=\text{E}}^{\text{K}}\gamma_i\cdot I(\text{color} = i) \nonumber \\
+&\quad + \sum_{j=\text{Good}}^{\text{Ideal}}\delta_j \cdot I(\text{cut} = j) \nonumber \\
+&\quad + \sum_{k=\text{SI2}}^{\text{IF}} \theta_k \cdot I(\text{clarity} = k).
 \end{align}
 
-## Model justification{#sec-justification}
-为什么选择glm，以及为什么选择gamma，因为data section 里reponse符合分布
+- $\beta_0$: Intercept term.
+- $\beta_1$: Coefficients of carat size, indicating the influence of carat weight of diamonds on the logarithmic space of price.  
+- $\gamma_i$: Coefficient of color in category $i$, where $i$ can be D, E, F, G, H, I, J, K.
+- $\delta_j$: Coefficient of cut in category $j$, where $j$ can be Ideal, Excellent, Very Good, Good.
+- $\theta_k$: Coefficient of clarity in category $k$, where $k$ can be IF, VVS1, VVS2, VS1, VS2, SI1, SI2.
+- $I$: Indicator function, used for dummy variable coding of classified variables.
+Its function is to judge whether the condition in parentheses is true.
+If the condition is true, the function takes the value of 1; otherwise, it takes the value of 0.
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+Since the response variable `price` is standardized and exponential-transformed and log-transformed during modeling, predicting the price requires reversing these transformations by only applying the inverse of the standardization because exponential-transformed and log-transformed cancel each other.
+Thus, the formula for predicting the price is (4):
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+\begin{align}
+\text{price} &= \log(\text{price}) \cdot \sigma + \mu.
+\end{align}
 
-## Model Comparision: Generalized Linear Model vs. Linear Model {#sec-compare}
+-   $\sigma$: the standard deviation of price in the training data, which is 2442.597.
+-   $\mu$: the mean of price in the training data, which is 4010.706.
+
+## Model Justification{#sec-justification}
+
+We expect a positive relationship between predictors (carat size, cut, color and  clarity) and response variable price.
+To test this relationship, we chose the Generalized Linear Model (GLM) with a Gamma distribution and a log link function.
+For categorical predictors like color, clarity, and cut, by setting the lowest quality levels (e.g., K for color, SI2 for clarity, and Good for cut) as reference levels, we can directly interpret the coefficients as the incremental effect of higher-quality levels on diamond prices.
+For continuous predictor carat size, we can interpret the coefficients in the model as how it influence diamond prices.
+This setup also aligns with our expectation that higher-quality diamonds (in terms of color, clarity, and cut) will positively influence price.
+
+The Generalized Linear Model (GLM) was chosen for its flexibility and ability to handle diverse response variable distributions.
+Unlike traditional linear models, which require normally distributed response variables, the GLM accommodates non-normal distributions, making it particularly well-suited for our data where the response variable, diamond price, follows a Gamma distribution, as shown in @fig-price.
+By specifying the log link function, the GLM captures the nonlinear relationship between the response variable and predictors, allowing for better modeling of the price variability while maintaining interpret ability and precision.
+
+Despite its advantages, the GLM has potential limitations and may not be suitable in certain scenarios.
+When the distribution of response variable is hard to observe, we may not able to assume its distribution.
+Furthermore, highly nonlinear relationships may not be adequately captured by the specified link function, requiring alternative modeling approaches.
+
+Furthermore, to validate and evaluate the model, a test dataset was used to calculate key metrics such as Root Mean Squared Error (RMSE), Mean Absolute Error (MAE), and Mean Squared Error (MSE).
+These metrics quantify the model's predictive accuracy and help identify potential areas of improvement.
+And the predicted values and the actual values are visualized and diagnostics are presented.
+These details are provided in @sec-model-details.
+
+## Model Comparision {#sec-compare}
+
+In addition to the generalized linear model, we also explore and compare alternative models, including linear regression and Bayesian regression.
+
+a. Linear Regression Model:
+
+The advantage of Linear model is that the results are easy to explain, and it can provide accurate parameter estimation under the condition of satisfying basic assumptions (such as linear relationship, normality, independence and variance homogeneity).
+However, its disadvantage is that the assumptions of the data are strict, and when the data violates these assumptions, the estimation of the model may be invalid.
+We use linear regression model implemented using the `lm` function in @citeR and use training dataset for model fitting and test dataset for model evaluation.
+
+b. Bayesian regression Model:
+
+The advantage of Bayesian model lies in its flexibility, which is especially suitable for scenes with less data, complex distribution or the need to combine prior knowledge.
+However, the disadvantage of Bayesian model lies in its high computational complexity, and improper selection of prior distribution may significantly affect the inference results.
+We also use the Bayesian Regression model to analyze the relationship between diamond prices and various predictors, implemented using the `stan_glm` function from the rstanarm package (@rstanarm) in @citeR.
+The model assumes a Gamma family with a log link function, and the priors are specified as weakly informative: normal distributions (mean = 0, standard deviation = 10) for both the coefficients and intercept, and an exponential distribution (rate = 3) for the auxiliary parameter.
+
+c. Comparision Result:
+
+@tbl-modelcompare shows that the Generalized Linear Model (GLM) outperforms the other models in both predictive accuracy and model parsimony.
+The GLM achieved the lowest Mean Squared Error (MSE) of 1.627, Mean Absolute Error (MAE) of 0.517, and Root Mean Squared Error (RMSE) of 1.276, indicating superior performance in predicting the scaled and transformed diamond prices.
+Furthermore, it also has the lowest Akaike Information Criterion (AIC) of 962.513 and Bayesian Information Criterion (BIC) of 1068.332, suggesting that it provides a more parsimonious fit to the data compared to the other models.
+In contrast, the Linear Model (LM) and Bayesian model demonstrated notably poorer performance.
+The LM exhibited an MSE of 2.231, an MAE of 0.954, and an RMSE of 1.494, while the Bayesian model displayed an MSE of 6.255, an MAE of 1.775, and an RMSE of 2.501, all significantly higher than the GLM's metrics.
+Additionally, the AIC and BIC scores for the LM were 6685.589 and 6791.408, respectively, reflecting both higher complexity and inferior predictive power.
+The Bayesian model, however, lacked calculable AIC and BIC values.
+The Bayesian model's AIC and BIC values are `NA` because `rstanarm` does not natively calculate these metrics.
+AIC and BIC are traditionally based on maximum likelihood estimation (MLE), which is not directly applicable to Bayesian models that rely on posterior distributions rather than MLE.
+Instead, Bayesian models are typically evaluated using metrics like the Deviance Information Criterion (DIC) or the Watanabe-Akaike Information Criterion (WAIC), which are designed to work with posterior distributions.
 ```{r}
@@
 #| label: tbl-modelcompare
-#| tbl-cap: "Model Reulst: Prediction of Diamond Price based on Color, Cut, Clarity and Carat Size"
+#| tbl-cap: "Model Comparison Metrics for GLM, LM, and Bayesian Models"
 #| warning: false
-aic_value <- AIC(model_glm)
-bic_value <- BIC(model_glm)
+
+#Prepare test data
+test_data <- read_parquet(here("data/02-analysis_data/diamondprice_test_data.parquet"))
+
+test_data$price <- scale(test_data$price, center = TRUE, scale = TRUE)
+test_data$price<-exp(test_data$price)
+test_data$color <- factor(test_data$color)
+test_data$cut <- factor(test_data$cut)
+test_data$clarity <- factor(test_data$clarity)
+
+# Find predictions based on 2 models
+predictions_glm <- predict(model_glm, newdata = test_data, type = "response")
+predictions_lm <- predict(model_lm, newdata = test_data)
+predictions_bayes <- predict(model_bayes, newdata = test_data)
+
+# Calculate MSE
+mse_glm <- mean((test_data$price - predictions_glm)^2)
+mse_glm <- round(mse_glm, 3)
+mse_lm <- mean((test_data$price - predictions_lm)^2)
+mse_lm <- round(mse_lm, 3)
+mse_bayes <- mean((test_data$price - predictions_bayes)^2)
+mse_bayes <- round(mse_bayes, 3)
+
+# Calculate MAE
+mae_glm <- mean(abs(test_data$price - predictions_glm))
+mae_glm <- round(mae_glm, 3)
+mae_lm <- mean(abs(test_data$price - predictions_lm))
+mae_lm <- round(mae_lm, 3)
+mae_bayes <- mean(abs(test_data$price - predictions_bayes))
+mae_bayes <- round(mae_bayes, 3)
+
+# Calculate RMSE
+rmse_glm <- sqrt(mse_glm)
+rmse_glm <- round(rmse_glm, 3)
+rmse_lm <- sqrt(mse_lm)
+rmse_lm <- round(rmse_lm, 3)
+rmse_bayes <- sqrt(mse_bayes)
+rmse_bayes <- round(rmse_bayes, 3)
+
+# Find AIC and BIC
+aic_glm <- AIC(model_glm)
+aic_glm <- round(aic_glm, 3)
+aic_lm <- AIC(model_lm)
+aic_lm <- round(aic_lm, 3)
+aic_bayes <- AIC(model_bayes) # NA
+bic_glm <- BIC(model_glm)
+bic_lm <- BIC(model_lm)
+bic_bayes <- BIC(model_bayes) # NA
+
+# Combine results into a data frame for summary
+model_comparison <- data.frame(
+  Model = c("GLM", "LM", "Bayesian"),
+  MSE = c(mse_glm, mse_lm, mse_bayes),
+  MAE = c(mae_glm, mae_lm, mae_bayes),
+  RMSE = c(rmse_glm, rmse_lm, rmse_bayes),
+  AIC = c(aic_glm, aic_lm, NA),
+  BIC = c(bic_glm, bic_lm, NA)
+)
+
+knitr::kable(model_comparison, format = "pipe")
 
@@
 
-## Model Evaluation{#sec-evaluation}
-See appendix
+# Results{#sec-result}
 
-# Results{#sec-result}
-## Model Result{#sec-modelresult}
+@fig-modelresults shows the relative contribution of carat weight, color, cut and clarity to the diamond price after standardization and exponential transformation and logarithmic transformation.
+And @fig-modelresults also visualizes the estimated regression coefficient of each variable and its 95% confidence interval.
+We can find:
+-   Carat Size: Carat weight has the most significant positive impact on diamond price, with a regression coefficient of 3.73.
+This indicates that as carat weight increases, the diamond price rises, which aligns with expectations.
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Model Reulst: Prediction of Diamond Price based on Color, Cut, Clarity and Carat Size"
-#| warning: false
+-   Color: Higher-grade colors (e.g., D) have the largest positive impact on diamond prices, with a coefficient of 1.343 for color D compared to the baseline (K, the lowest grade).
+Lower-grade colors (e.g., J and I) have progressively smaller positive coefficients, suggesting that price increases are more obvious for diamonds with higher color grades.
 
-# 获取 model_glm 的系数摘要
+-   Clarity: Similar to color, higher clarity grades (e.g., IF and VVS1) positively influence diamond prices.
+For instance, the coefficient for clarity IF is 0.926, while VVS1 is 0.896, compared to the baseline clarity grade (SI2).
+Lower clarity grades (closer to the baseline) have relatively smaller positive coefficients, showing their lesser contribution to price increases.
+
+-   Cut: Cut quality has a smaller impact compared to other factors.
+For example, the "Ideal" cut has a coefficient of 0.216, which indicates a slight positive impact compared to the baseline ("Good" cut).
+Similarly, "Excellent" and "Very Good" cuts contribute marginally to price increases.
+
+-   Intercept: The intercept of -4.805 represents the baseline value of diamond price (after transformation) when all predictors are at their reference levels (i.e., K for color, SI2 for clarity, and Good for cut).
+
+In summary, carat weight has the most significant impact on diamond prices, followed by clarity and color, while cut quality has a relatively smaller effect.
+These results suggest that buyers prioritize carat weight and the diamond's visual attributes (color and clarity) over the precision of the cut.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
+#| label: fig-modelresults
+#| fig-cap: "Model Results"
+
+# Get the coefficients and their confidence intervals
 model_summary <- summary(model_glm)$coefficients
+model_summary_df <- as.data.frame(model_summary)
+model_summary_df$Predictors <- rownames(model_summary_df)
 
-# 将摘要转换为数据框，便于 knitr::kable 格式化
-model_summary_df <- as.data.frame(model_summary)
-summary(model_glm)
-# 使用 knitr::kable 输出表格
-knitr::kable(
-  model_summary_df,
-  digits = 3,  # 设置小数点后保留 3 位
-  format = "pipe"  # 输出格式，可选 "html", "latex", "pipe" 等
-)
+# Calculate 95% confidence intervals
+model_summary_df$CI_Lower <- model_summary_df$Estimate - 1.96 * model_summary_df$`Std. Error`
+model_summary_df$CI_Upper <- model_summary_df$Estimate + 1.96 * model_summary_df$`Std. Error`
+
+# Create the plot
+ggplot(model_summary_df, aes(x = Estimate, y = reorder(Predictors, Estimate))) +
+  geom_point(color = "palevioletred") +  # Coefficients as points
+  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) +  # Confidence intervals
+  geom_text(aes(label = round(Estimate, 3)), hjust = -0.3, size = 3) +  # Lable estimates
+  theme_minimal() +  # Minimal theme
+  labs(
+    x = "Coefficient Estimate",
+    y = "Predictors"
+  ) + 
+  theme(axis.text.y = element_text(size = 8))  # Adjust y-axis text size
+
 ```
 
-## Predictions vs Actual Value{#sec-predictions}
+## Example of Prediction{#sec-example}
+
+# Discussion{#sec-discussion}
+
+## Exploration of Model Result {#sec-exploration}
+
+This study examines how key features of diamonds, such as carat size, color, clarity, and cut, influence their prices.
+The results show that carat weight has the most significant impact on diamond prices, followed by clarity and color, while cut quality has a relatively smaller effect.
+These findings highlight the preferences and values that drive consumer behavior and shape industry practices.
+By understanding the role of each predictor, we can explore the deeper social and cultural meanings behind these choices, such as the importance of visibility, aesthetics, and societal expectations in defining value.
+
+Carat size has the strongest impact on price.
+Larger diamonds are often associated with wealth, success, and love, making them highly desirable for significant events like engagements and weddings.
+This focus on size shows how people value physical attributes that are easily noticeable, often linking material possessions to social status and personal achievements.
+Economically, the preference for size drives demand for larger diamonds, encouraging industries to focus on producing and marketing them as rare and valuable.
+
+Color and clarity also have a strong effect on price.
+Higher grades in these features lead to much higher prices, which shows that buyers are willing to pay more for diamonds that look perfect or flawless.
+Even though these differences might not always be noticeable to the average person, marketing and cultural standards make these traits seem important.
+This focus influences how diamonds are graded and priced, creating a market where beauty and perfection are key drivers of value.
+
+Cut, while important for a diamond's brilliance, has a smaller impact on price compared to the other features.
+This suggests that buyers may undervalue the craftsmanship behind the cut, focusing instead on features like size and color that are easier to see and compare.
+This pattern is common in luxury markets, where visible traits often matter more than technical quality or skill.
+
+In conclusion, diamond prices are influenced by a mix of consumer behavior, cultural values, and industry practices.
+Buyers tend to value features that are visible and easy to compare, driving demand and shaping market trends.
+This study shows how societal values influence pricing and production, not only in the diamond market but also in other areas of the luxury goods industry.
+
+## Limitations{#sec-limitation}
+
+### Data Limitations{#sec-datalimit}
+
+Although the data set is valuable, there are several limitations, which affect the universality and depth of the research results.
+A key limitation is the limited price range, which only includes diamonds with a price between $1,000 and $10,000.
+This does not include low-priced and high-end luxury diamonds, which may miss the unique pricing model of these market segments.
+In addition, the price distribution is seriously tilted to the right, and most of the prices are concentrated between 2500 and 5000 dollars.
+This imbalance may lead to deviation in the analysis, because diamonds with higher prices may be affected by different market factors and their representation is insufficient.
+
+Another limitation is that the data set narrowly focuses on physical properties, such as carat size, color, clarity and cutting, while ignoring background factors such as brand reputation, certification sources and market trends.
+These external factors will significantly affect pricing, but they are not taken into account in the data.
+In addition, the data set lacks geographical and cultural details, which can provide insights into regional differences in preferences and needs.
+This omission limits the global applicability of the research results, because diamond pricing often varies with the market and consumer base.
+
+The dataset also simplifies some predictor variables, particularly cut quality, by classifying them into broad groups (Ideal, Excellent, Very Good, and Good) without accounting for finer details like proportions or symmetry.
+These details, such as the arrangement of facets or crown angles, are crucial for evaluating a diamond's brilliance and could provide a deeper explanation for price variations.
+Similarly, the color and clarity variables are not fully represented.
+For instance, diamond color is graded from D (colorless) to Z (light yellow or brown), but the dataset only includes colors from D to K, leaving out lower-grade colors that could provide additional insights.
+Moreover, the absence of time-related factors limits the ability to analyze how diamond prices change over time due to shifts in consumer preferences, market trends, or seasonal effects.
+
+Finally, the data set shows the potential problems of imbalance and lack of diversity.
+For example, a lower quality cut (good) and a lower color grade (k) are insufficient, which may lead to distorted results and limit the ability to draw conclusions about these groups.
+In addition, if the data set comes from a single retailer or region, the results may reflect localized pricing strategies or consumer preferences, rather than broader market trends, thus reducing its generalization to other environments.
+
+### Model Limitations{#sec-modellimit}
+One limitation of the GLM model is its inability to fully capture the complexity of diamond price variability due to its fixed distributional assumptions.
+The use of the Gamma distribution with a log link function, while appropriate for positive and skewed data, may oversimplify the true underlying patterns in the data.
+This is particularly evident in higher price ranges, where the model underestimates prices.
+
+Another limitation is in how the predictors are handled.
+The model treats clarity, color, and cut as categorical variables divided into broad categories, which simplifies their complexity.
+For example, subtle variations within a clarity grade or interactions between attributes, like how cut quality might impact price differently depending on carat size, are not accounted for.
+These oversimplifications may prevent the model from capturing more detailed relationships, potentially reducing its predictive accuracy.
+
+## Futurer Direction {#sec-further}
+To improve the depth and reliability of future research, several enhancements to the dataset and model can be considered.
+Expanding the price range to include both low-cost and luxury diamonds would provide a broader view of pricing patterns across the market.
+Additionally, addressing imbalances by incorporating underrepresented categories, such as lower-quality cuts and color grades, would reduce bias and improve generalizability.
+We could also include additional predictors, such as cut proportions, symmetry, and time, to enable a more detailed analysis of pricing factors and facilitate the study of price trends over time, including seasonal effects, and market fluctuations.
+The model can be improved by adopting more flexible approaches, such as generalized additive models (GAMs) or Bayesian hierarchical models, which can better handle non-linear relationships and interactions between predictors.
+These methods are particularly useful for capturing complex patterns in data, especially in higher price ranges.
+And to address variability and outliers, techniques like robust regression or weighted least squares can help manage non-constant variance in residuals, while carefully identifying and examining influential points can reduce their impact on predictions.
+
+\newpage
+
+\appendix
+
+# Appendix {-}
+
+# Additional Model details {#sec-model-details}
+
+## Predicted Diamond Prices {#sec-predictions}
+
+@fig-prediction_actual compares the predicted prices from the GLM model (blue line) with the scaled and transformed prices from the test dataset (red points).
+It is important to note that the prices shown in the plot are not the actual diamond prices.
+The response variable, `price`, was first scaled using z-score normalization and then exponentiated.
+Additionally, the predictions from the GLM model were transformed using a log link function, which is consistent with the assumptions of the Gamma distribution.
+
+The GLM model captures the general trend of the transformed prices well, especially in the lower and middle ranges.
+The predicted values closely follow the transformed prices in these areas, indicating that the GLM model performs well for most of the data.
+However, at higher transformed price levels, the predictions tend to underestimate the values, as indicated by the wider spread of red points compared to the smoother blue line.
+The variability of the transformed prices increases at higher indices, but the model does not fully capture this.
+This suggests that the GLM model, with its fixed Gamma distribution and log link function, may oversimplify the behavior of the response variable in these regions.
+The underestimation at higher levels highlights potential limitations in the model’s assumptions.
+
+In summary, while the GLM model effectively models the scaled and transformed price data for most observations, it struggles to account for the increasing variability in higher ranges.
+Further refinements, such as addressing variability or investigating the suitability of the distributional assumptions, could improve the model’s performance.
 
@@
 #| fig-cap: "Actual vs Predicted Values"
+test_data <- read_parquet(here("data/02-analysis_data/diamondprice_test_data.parquet"))
 
@@
     x = "Index",
-    y = "Price"
+    y = "log(scale(Price)"
   ) +
@@
 
-## Example of Prediction{#sec-example}
+## Evaluation Metrics {#sec-evaluation}
 
-# Discussion{#sec-discussion}
+@fig-metrics shows how the Generalized Linear Model (GLM) was evaluated on the test dataset using three key metrics: Mean Squared Error (MSE), Mean Absolute Error (MAE), and Root Mean Squared Error (RMSE).
+The MSE of 1.627 indicates that the overall squared differences between the predicted and actual diamond prices are relatively small, suggesting that the model captures the relationship between the predictors and the response variable reasonably well.
+However, since MSE amplifies the impact of larger errors, it is complemented by RMSE for better interpret ability.The MAE of 0.517 shows that, on average, the absolute difference between the predicted and actual values is low.
+This highlights the model's strong ability to provide accurate predictions in most cases and reflects that its performance is not heavily skewed by outliers.
+Compared to MSE, MAE is less sensitive to extreme errors, offering a more balanced perspective on prediction accuracy.
+The RMSE of 1.276, being the square root of MSE, provides a direct measure of the standard deviation of prediction errors in the original data's units.
+While RMSE tends to be slightly higher than MAE because it gives more weight to larger errors, its relatively low value confirms the model's stability and reliable performance on the test data.
+However, the gap between RMSE and MAE suggests the presence of some larger errors or outliers that may require further investigation.Overall, these metrics indicate that the GLM performs well in predicting diamond prices, with reasonable accuracy and controlled error levels.
 
-## First discussion point {#sec-first-point}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
+#| label: fig-metrics
+#| fig-cap: "GLM Model Metrics"
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Limitations{#sec-limitation}
-### Data Limitations{#sec-datalimit}
-数据分布不均
-### Model Limitations{#sec-modellimit}
-
-## Further Considerations{#sec-further}
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details {#sec-addtionaldata}
-
-## Data Cleaning{#sec-dataclean}
-data section
-## Data Preparation and Data Split{#sec-dataprepare}
-Model Section
-
-response variable
-train test to fit the mode
-
-# Additional Model details {#sec-model-details}
-
-## Evaluation Metrics and Diagnostic Table{#sec-evaluation}
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
-#| label: fig-evaluation
-#| fig-cap: "Actual vs Predicted Values"
-
-# 加载必要的库
-library(knitr)
-
-# 假设 `model_glm` 是基于 `train_data` 构建的模型
-# 假设 `test_data` 是用于测试的独立数据集
-
-# 1. 使用 test_data 计算 MSE 和 MAE
-predicted_test <- predict(model_glm, newdata = test_data, type = "response")
-actual_test <- test_data$price  # 假设价格列为 'price'
-
-# 计算 MSE 和 MAE
-mse_test <- mean((predicted_test - actual_test)^2)
-mae_test <- mean(abs(predicted_test - actual_test))
-
-# 2. 基于 train_data 的 R² 和 Adjusted R²
-# 计算总平方和和回归平方和
-actual_train <- train_data$price
-predicted_train <- predict(model_glm, newdata = train_data, type = "response")
-
-ss_total <- sum((actual_train - mean(actual_train))^2)
-ss_residual <- sum((actual_train - predicted_train)^2)
-
-# 计算 R² 和 Adjusted R²
-r_squared <- 1 - (ss_residual / ss_total)
-n <- nrow(train_data)
-p <- length(coef(model_glm)) - 1  # 模型中的预测变量数量
-adjusted_r_squared <- 1 - ((1 - r_squared) * (n - 1) / (n - p - 1))
-
-# 3. 计算过度离散性
-dispersion_ratio <- deviance(model_glm) / df.residual(model_glm)
-
-# 4. 将结果格式化为表格
-
-# 结果 1：基于测试集的 MSE 和 MAE
-test_results <- data.frame(
-  Metric = c("MSE (Test)", "MAE (Test)"),
-  Value = c(mse_test, mae_test)
+# Organize GLM data into a table
+glm_metrics <- data.frame(
+  Metric = c("MSE", "MAE", "RMSE"),
+  Value = c(mse_glm, mae_glm, rmse_glm)
 )
 
-# 结果 3：过度离散性: summary(model)里面有
-dispersion_result <- data.frame(
-  Metric = "Dispersion Ratio",
-  Value = dispersion_ratio
-)
-
-# 使用 knitr::kable 将表格输出
-cat("### Test Data Results\n")
-kable(test_results, caption = "Performance Metrics on Test Data", digits = 3)
-
-cat("\n### Dispersion Check\n")
-kable(dispersion_result, caption = "Overdispersion Check", digits = 3)
-
-```
-
-## Feature importance analysis{#sec-importance}
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-feature_importance
-#| layout-ncol: 2
-#| fig-cap: "Feature importance analysis"
-
-library(broom)
-
-coefficients <- tidy(model_glm)
-ggplot(coefficients, aes(x = reorder(term, estimate), y = estimate)) +
-  geom_bar(stat = "identity", fill = "lightblue") +
-  coord_flip() +
-  labs(title = "Variable Importance", x = "Variables", y = "Estimates") +
-  theme_minimal()
+# Use knitr::kable to format the table
+knitr::kable(glm_metrics, format = "pipe", col.names = c("Metric", "Value"))
 
@@
 ## Diagnostics{#sec-diagonsis}
+
+@fig-diag from the GLM model shows how well the model performs and whether it follows the key assumptions of the Gamma distribution with a log link.
+
+The "Residuals vs.
+Fitted" plot indicates a slight curvature in the residuals, particularly at lower fitted values, suggesting potential non-linearity or slight misspecification in the link function.
+Additionally, the spread of residuals increases slightly for higher fitted values, hinting at heteroscedasticity (non-constant variance).
+Ideally, residuals should be randomly scattered around zero with no discernible pattern.
+
+The Q-Q plot assesses whether the residuals conform to the theoretical Gamma distribution.
+While most points follow the diagonal line, deviations are observed in the upper quantiles, with several extreme residuals identified (e.g., points 1930, 1899).
+These deviations shows that the model may not fully capture the response variable's distribution or that outliers are present.
+
+The Scale-Location plot further supports evidence of heteroscedasticity, as the variance of residuals increases with higher fitted values.
+Ideally, the points should be evenly spread around the horizontal line, but the observed increase in variance indicates that the model might benefit from additional adjustments to better handle variability in the response variable.
+
+The "Residuals vs.
+Leverage" plot highlights a few potentially influential points (e.g., 1930, 1899, 1924) with higher leverage.
+Although none of these points exceed Cook’s distance thresholds, their presence warrants closer examination to ensure they do not disproportionately affect the model.
+
+In summary, the model performs well but shows slight heteroscedasticity and deviations from the Gamma distribution. Addressing these issues and checking outliers may improve reliability and accuracy.
 
@@
 #| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Diagonsis"
+#| label: fig-diag
+#| fig-cap: "Diagnostics"
 
-par(mfrow = c(2, 2))  # 生成 2x2 子图布局
+par(mfrow = c(2, 2))
 plot(model_glm)

### 2024-12-03 others/datasheet/datasheet_template.qmd
complete datesheet

---
title: "Datasheet for 'Diamond dataset'"
author: 
  - Yawen Tan
thanks: "Code and data are available at:  [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references .bib
---

Extract of the questions from @gebru2021datasheets.

The dataset discussed in this datasheet is 'Diamonds' [@diamonds_data].

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The primary purpose of the dataset is to assess the contributions of key factors—such as carat size, diamond color, cut, and clarity—to variations in the diamond price. Additionally, it aims to provide accurate predictions of diamond prices based on these features. 
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was compiled by Lou Valente, associated with JMP, a statistical software suite developed by SAS Institute.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The available information does not specify any particular funding sources or grants associated with the creation of this dataset.
4. *Any other comments?*
    - This dataset is a valuable resource for statistical analysis and educational purposes, offering insights into the relationships between various diamond characteristics and their market prices. It serves as a practical example for applying multiple regression techniques and other analytical methods.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances in the dataset represent individual diamonds, each characterized by various attributes such as weight, quality, and price. All instances belong to the same category (diamonds), with no distinct types beyond this.
2. *How many instances are there in total (of each type, if appropriate)?*
	- The dataset contains 2,690 instances in total, with each instance representing a unique diamond.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of diamonds rather than a comprehensive collection of all diamonds globally. It is not explicitly stated whether the sample is random, but given that the data was collected from the internet, it is likely to be a convenience sample. Representativeness in terms of geographic coverage or market diversity is not validated.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of processed features describing a diamond. The features include: Carat weigh, Cut quality, Color grade, Clarity grade, Price (in monetary units). These features allow for statistical and predictive modeling.

5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Yes, the dataset includes the "price" of each diamond as the target variable. This label allows for regression analysis to predict price based on the diamond's attributes.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- There is no explicit indication of missing data in the Diamonds dataset. Each instance includes complete information for all features (carat, cut, color, clarity, and price). However, if missing values exist, they might not have been explicitly documented.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No, the dataset does not explicitly represent relationships between instances. Each diamond is treated as an independent observation with no inherent links to other diamonds.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- The dataset does not come with predefined splits for training, validation, or testing. Users can create their own splits based on their specific analysis or modeling needs, such as stratifying by cut or price range to ensure balanced subsets.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The dataset does not explicitly report errors or redundancies, but potential sources of noise include subjective grading (e.g., cut, color, clarity) that could vary depending on the evaluator. Additionally, data collected from the internet might introduce inconsistencies due to differences in recording or reporting standards.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained and does not rely on external resources for its attributes. There are no references to external links, archival versions, or licensing constraints for the dataset itself. However, its description notes that the data was collected from the internet, suggesting it might originally have referenced external resources no longer linked directly.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No, the dataset does not contain any confidential data. It only includes information about diamonds, such as their physical and qualitative characteristics, which are not protected by legal privilege or confidentiality agreements.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No, the dataset does not contain any offensive, insulting, or threatening content. It focuses solely on diamond properties and prices, which are neutral and non-sensitive in nature.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The dataset does not explicitly identify human sub-populations such as age or gender. However, it does categorize diamonds by subgroups such as cut quality, color grade, and clarity grade. These attributes can be viewed as "sub-populations" within the data, describing the distribution of diamonds across different categories.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, it is not possible to identify individuals from this dataset. The data pertains to diamonds and not to any personal or identifying information about individuals.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No, the dataset does not include sensitive information. It only contains technical and market attributes of diamonds, which are not associated with personal, biometric, or other sensitive data.
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was indirectly sourced from the internet, likely collected from commercial and market listings for diamonds. It represents observable characteristics (e.g., carat, cut, color, clarity) and their corresponding prices. The description does not specify validation or verification processes, so the reliability of the source data remains uncertain.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data collection was done manually or via software scripts to extract information from online resources. The exact mechanisms or validation procedures used during collection are not explicitly detailed.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset appears to be a convenience sample, extracted from available online data without explicit mention of a probabilistic or systematic sampling strategy. It is unclear if the sample was designed to be representative of the entire diamond market.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The dataset was compiled by Lou Valente, associated with JMP. The details regarding additional personnel involved or compensation methods are not provided.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The timeframe for data collection is not specified. However, given that it was sourced from the internet, it is reasonable to assume the data reflects market conditions close to the period of collection, aligning roughly with the dataset's creation. Further details on the exact dates are not available.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No explicit mention of ethical review processes, such as an institutional review board (IRB), is provided for this dataset. Since the data pertains to commodities (diamonds) rather than individuals, ethical reviews were likely deemed unnecessary.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was obtained via third-party sources, specifically collected from the internet (likely from online diamond retailers or market databases).
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Not applicable, as the dataset does not involve individuals or personal data
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Not applicable, as the dataset does not involve personal data or interactions with individuals.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Not applicable, as no personal data or consent process is involved.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No, such analysis is not applicable as the dataset does not involve data subjects. It focuses solely on diamonds, which are inanimate objects with no associated ethical or personal implications.
12. *Any other comments?*
	- No

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- The dataset appears to have undergone preprocessing to ensure that each instance includes the relevant attributes (carat, cut, color, clarity, and price). Categories such as cut, clarity, and color have been labeled into discrete values to facilitate analysis. There is no indication of missing data, suggesting that missing values were either imputed or removed. However, detailed information on the preprocessing steps is not provided.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- There is no mention of the availability of raw data. The dataset provided represents the preprocessed and cleaned version suitable for analysis.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The dataset does not include information about the software or tools used for preprocessing. It is likely that manual curation or commonly available statistical tools were employed, but no specific tools are documented.
4. *Any other comments?*
	- The dataset is user-ready and appears to be cleaned and well-structured for statistical modeling. While preprocessing details are not explicitly documented, the data format suggests that steps were taken to enhance usability.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The dataset has been widely used in educational contexts for teaching statistical techniques, such as multiple regression analysis and exploratory data analysis. It is commonly used in tutorials, workshops, and data science courses to demonstrate relationships between variables.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- There is no dedicated repository linking to all works or systems that have used the dataset. However, it is frequently referenced in statistical software packages like R (e.g., ggplot2) and appears in various online educational materials and textbooks
3. *What (other) tasks could the dataset be used for?*
	- Potential tasks include: Feature engineering exercises to create new attributes or improve existing models; Clustering or segmentation analyses to identify groups of similar diamonds.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The dataset's reliance on data collected from the internet introduces potential biases, as it may not represent the entire diamond market or regional variations. Users should consider the potential limitations in representativeness and avoid drawing overly general conclusions about the global diamond market. This can be mitigated by combining this dataset with more comprehensive or diverse data sources.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for: 1. Drawing inferences about human populations, as it is unrelated to individuals or social demographics. 2. Legal or financial decisions involving real-world diamond markets without validating its representativeness or currency. 3. High-stakes decisions where data accuracy or completeness is critical, as the dataset might not capture all nuances of the diamond industry.
6. *Any other comments?*
	- No

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset is publicly available and distributed via the Data and Story Library (DASL) website. It is openly accessible to anyone for educational and analytical purposes.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed through the DASL website as a downloadable file. It does not appear to have a digital object identifier (DOI).
3. *When will the dataset be distributed?*
	- The dataset is already available and has been publicly distributed for an extended period. It is accessible at any time through the DASL website.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset does not explicitly mention a copyright or specific licensing terms. However, its inclusion on the DASL website implies it is intended for free and open use, primarily for educational and research purposes. Users should verify terms of use on the DASL platform for clarity.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No known IP-based or third-party restrictions are associated with this dataset. It is freely shared for public use via DASL.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No, there are no export controls or regulatory restrictions applicable to this dataset. It is unrestricted and available globally.
7. *Any other comments?*
	- No

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset is hosted and maintained by the Data and Story Library (DASL), which is an educational resource for statistical data.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- There is no direct contact information provided for the dataset’s owner or curator. Users can visit the DASL website for more information or to make inquiries.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no specific mention of an erratum for the Diamonds dataset on the DASL website.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- There is no indication that the dataset will be updated. It appears to be static and provided as-is for educational purposes. Updates, if any, would likely need to be communicated through the DASL platform.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Not applicable, as the dataset does not involve personal or human-related data.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Since the dataset is static and does not appear to have multiple versions, the question of supporting older versions is not applicable.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- No explicit mechanism for contributions or extensions is mentioned. Users can, however, utilize the dataset freely for their analyses and potentially create derivative datasets or studies based on it. Any such contributions would not be officially supported by DASL.
8. *Any other comments?*
	- No

\newpage

# References

### 2024-12-03 others/datasheet/datasheet_template.qmd
upload datasheet qmd and pdf

@@
 thanks: "Code and data are available at:  [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
 date: today
@@
 number-sections: true
-bibliography: references .bib
+bibliography: references.bib
 ---
@@
 Extract of the questions from @gebru2021datasheets.
-
 The dataset discussed in this datasheet is 'Diamonds' [@diamonds_data].

### 2024-12-03 scripts/05-exploratory_data_analysis.R
complete exploratory cleaned data

@@ -1,35 +1,52 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Explore the Cleaned Data
+# Author: Yawen Tan
+# Date: 2 December 2024
+# Contact: yawen.tan@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# - The `tidyverse`,`arrow`,`dplyr` package must be installed and loaded
+# - 03-clean_data.R must have been run
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
+library(arrow)
+library(dplyr)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
-
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+cleaned_data <- read_parquet(here("data/02-analysis_data/cleaned_diamondprice.parquet"))
 
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+#### Explore data ####
+
+#Find the category each variables
+
+variable_types <- sapply(cleaned_data, class)
+variable_types
+
+
+#Find the range of each variables
+
+# Categories Variable: color, cut, and clarity
+color_categories <- unique(cleaned_data$color)
+cut_categories <- unique(cleaned_data$cut)
+clarity_categories <- unique(cleaned_data$clarity)
+# Continuous Variablle: carat_size, price
+carat_min <- min(cleaned_data$carat_size, na.rm = TRUE)
+carat_max <- max(cleaned_data$carat_size, na.rm = TRUE)
+price_min <- min(cleaned_data$price, na.rm = TRUE)
+price_max <- max(cleaned_data$price, na.rm = TRUE)
[…]

### 2024-12-03 paper/paper.qmd
complete methodology and survey

@@
 
+# Idealized Methodology
+
+## Overview
+
+The purpose of this study is to explore the key factors affecting the price of diamonds, including carat weight, color, clarity and cut.
+Through multi-wave data collection and strict data quality control, the goal of this study is to build an accurate forecasting model and provide a deep understanding of market trends.
+The research method combines extensive sample recruitment, diversified data collection techniques and statistical modeling tools to provide reliable basis for quantitative analysis and qualitative interpretation.
+
+## SamplingApproach
+
+In this study, stratified random sampling method is used to ensure that the samples are representative enough.
+
+-   Stratification criteria include geographical area, income level and purchasing preference.
+-   The sample size is set to 3000 to meet the confidence level of 95% and the error range of 3%.
+-   Data sources include diamond retailers, auction platforms and online consumer surveys.
+
+## Recruitment
+
+Participants are recruited through the following channels:
+
+-   Cooperate with major jewelry retailers and market research institutions to obtain target group information through sales data.
+-   Put targeted advertisements on social media and email platforms to attract potential participants to fill in online surveys.
+-   Provide small cash rewards (such as $10 gift cards) or lucky draw opportunities to increase participation rate and reduce bias.
+
+All participants need to sign an electronic informed consent form to ensure that data collection conforms to ethical norms.
+
+## Data Collection and Survey Design
+
+Data is collected through various channels to ensure wide coverage and data quality:
+
+-   The online survey platform is used to collect consumers' purchasing behavior, preferences and socio-economic background data.
+-   Combined with the actual market data (such as transaction records), the questionnaire results are verified.
+
+The questionnaire design includes:
+-   Closed-form questions (multiple choice, Likert scale) to evaluate consumer preferences.
+-   Open-ended questions gain insight into the factors affecting prices.
+The questionnaire was optimized by small-scale pretest, focusing on reducing the ambiguity of questions and the fatigue of respondents
+
+## Data Validation and Quality Control
+
+-   In the data cleaning stage, incomplete and contradictory questionnaire responses were eliminated, and duplicate records were eliminated.
+-   Using outlier detection technology to identify and deal with possible problem data points.
+-   Re-verify key data points by tracking some interviewees to ensure the consistency and reliability of the answers.
+
+## Multi-Wave Data Collection and Aggregation
+
+In order to study market trends and price changes, data collection is divided into three waves, each with a quarterly interval:
+
+-   Wave 1: Obtain the data of consumers' price sensitivity and buying habits in peak sales season (such as festivals).
+-   Wave 2: Investigate the off-season market demand and price elasticity.
+-   Wave 3: verify the stability of the model, focusing on the analysis of the changing trend of bulk diamond buying behavior.
+
+The data are aggregated after standardization among waves to ensure the consistency of time series analysis.
+
+## Budget Allocation
+
+The total budget is estimated at $75,000.The allocation of funds is as follows:
+
+-   Sample recruitment and incentives (35%): including gift cards and advertising expenses.
+-   Data collection and processing (25%): Covers the cost of online platform and cleaning tools.
+-   Questionnaire design and pilot test (15%): design optimization and forecast trial expenditure.
+-   Data analysis and report writing (15%): including software use and labor costs.
+-   Quality control (10%): data verification and tracking verification costs.
+
+# Idealized Survey
+
+The idealized survey questionnaire can be accessed via the following link:
+
+https://docs.google.com/forms/d/e/1FAIpQLSe9YMFwC4RHHg36c1VY8yA-cZpdrN32yZfeCMJf_jD3qweOQg/viewform?usp=sf_link
+
+## Survey Questions
+
+**Demographic Questions**:
+
+1. What is your age? (open)
+
+2. What's your gender? (M/F/Other)
+
+3. What is your main source of income? (Fixed income/freelance/other)
+
+**Behavioral Patterns**:
+
+4. How often did you buy diamonds in the past year? (Never/once /2-3 times/more than 3 times)
+
+5. Where do you prefer to buy diamonds? (Holiday gifts/engagement or marriage/investment/other)
+
+**Perceptions and Attitudes**:
+
+6. Which of the following do you think has the greatest influence on the price of diamonds? (carat/color/clarity/cut/brand)
+
+7. How do you evaluate the importance of the following diamond characteristics: carat size, color, clarity, cut? (1- very unimportant, 5- very important)
+
+**Outcome Measures**:
+
+8. Assuming the same price, which of the following diamonds would you prefer to buy? (Grade D color /IF clarity /1.5 carats)
+
+9. Please rate your satisfaction with the last diamond purchase (1- very dissatisfied, 5- very satisfied).
+
+**Open-Ended Questions**
+:
+10. What do you think are the main challenges in the diamond market at present?
+
+11. Please describe the main reason why you choose a diamond.
+
 \newpage

### 2024-12-04 paper/paper.qmd
Update introduction

@@
 钻石质量的 4C标准，即评判钻石的通用标准：颜色、切割、净度和克拉重量。
+
+# Introduction
+
+The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper.
+A reader should be able to read only the introduction and know what was done, why, and what was found.
+Likely 3 or 4 paragraphs.
+
+钻石质量的 4C标准，即评判钻石的通用标准：颜色、切割、净度和克拉重量。
+estimand
+
+Recent advancements in data analytics and machine learning have enabled more precise predictions of diamond prices based on their features.
+For instance, research published in the International Journal of System Assurance Engineering and Management(@Basha2024), evaluates 23 machine learning models, including regression techniques, to predict diamond prices.
+The study shows the effectiveness of models like CatBoost Regressor and XGBoost Regressor in achieving high accuracy after hyperparameter tuning.
+Similarly, @Sharma2021 also conducts a comparative analysis of multiple supervised machine learning models, identifying Random Forest Regressor as particularly effective in predicting diamond prices.
+Despite these advancements, there remains a need for analyses diamond price based on other models to enhance the accuracy and reliability of diamond price predictions.
+This research aims to fill this gap by employing a generalized linear regression model to show the significance of each of the 4Cs in determining diamond prices and to predict diamond prices.
+In this paper, Generalized Linear Model (GLM) with a Gamma distribution and log link function shows that carat weight exerts the strongest positive influence on price, followed by clarity and color, while cut has a relatively smaller impact.
+The predictive model demonstrates good performance on test data, showing its utility in forecasting diamond prices and understanding market patterns.
+The estimand of this study is the expected diamond price given specific attributes of carat weight, color, clarity, and cut.
+This quantifies the direct relationship between the predictors and the response variable, enabling precise and explicable predictions for stakeholders in the diamond market.
+
+### Background:
+
+### Research questions:
+
+This study focuses on identifying the significant factors influencing diamond prices and building a reliable regression model to predict prices based on diamond carat size, color, clarity and cut.
+
+### Research objectives:
+
+This study employs a Generalized Linear Model (GLM) with a Gamma distribution and log link function to examine how the 4Cs contribute to variations in diamond prices.The analysis shows that carat weight exerts the strongest positive influence on price, followed by clarity and color, while cut has a relatively smaller impact.
+The predictive model demonstrates good performance on test data, showing its utility in forecasting diamond prices and understanding market patterns.
+
+### Estimand
+The estimand of this study is the expected diamond price given specific attributes of carat weight, color, clarity, and cut.
+This quantifies the direct relationship between the predictors and the response variable, enabling precise and explicable predictions for stakeholders in the diamond market.
+
+### why important
+
+### structure
+The remainder of this paper is structured as follows.
+@sec-data discusses data overview, response variable, predictor variables, data measurement and data visualization which includes the plots of each variable and its response, as well as plots of variable interactions.@sec-model shows how to generate the generalized linear regression.
+@sec-result shows the relationship between carat size, color, cut and clarity in diamond price.
+@sec-discussion discusses the results of @sec-result going into detail which shows the complex relationship between sociocultural background and diamond price.
+And it also shows the limitations of research, and proposes the focus that future research should focus on to enhance the depth and accuracy of the research.
 

### 2024-12-04 paper/paper.qmd
update introduction of the paper

--- 2024-12-03 paper/paper.qmd
@@
 
-钻石质量的 4C标准，即评判钻石的通用标准：颜色、切割、净度和克拉重量。
+Diamonds have long symbolized luxury, romance, and prestige, with their valuation primarily determined by the Four Cs: Carat weight, Color, Clarity, and Cut.
+The Gemological Institute of America established this standard to assess diamond quality consistently worldwide.
+Each of these attributes uniquely influences a diamond's market value.
+Carat size measures the diamond's mass, with larger diamonds being rarer and typically more valuable.
+Color grading evaluates the absence of color, ranging from D (colorless) to Z (light yellow or brown), with colorless diamonds commanding higher prices.
+Clarity shows internal and external imperfections, where fewer inclusions and blemishes enhance value.
+Cut quality, particularly in round brilliant diamonds, affects light reflection and overall brilliance, significantly impacting aesthetic appeal and price (@GIA4Cs).
+While the 4Cs provide a framework for valuation, accurately predicting diamond prices remains complex due to the interplay of these characteristics and market dynamics.
+Recent advancements in data analytics and machine learning have enabled more precise predictions of diamond prices based on their features.
+For instance, research of @Basha2024 published in the International Journal of System Assurance Engineering and Management, evaluates 23 machine learning models, including regression techniques, to predict diamond prices.
+The study shows the effectiveness of models like CatBoost Regressor and XGBoost Regressor in achieving high accuracy after hyperparameter tuning.
+Similarly, @Sharma2021 also conducts a comparative analysis of multiple supervised machine learning models, identifying Random Forest Regressor as particularly effective in predicting diamond prices.
+Despite these advancements, there remains a need for analyses diamond price based on other models to enhance the accuracy and reliability of diamond price predictions.
+This research fills this gap by employing a Generalized Linear Model.
+
+This study focuses on identifying the significant factors influencing diamond prices and building a reliable model to predict prices based on diamond carat size, color, clarity and cut.
+The estimand is the expected diamond price given specific attributes of carat weight, color, clarity, and cut.
+We use the dataset of diamond price from DASL and use Generalized Linear Model (GLM) with a Gamma distribution and log link function to analysis.
+It shows shows that carat weight has the strongest positive influence on price, followed by clarity and color, while cut has a relatively smaller impact.
+The predictive Generalized Linear Model demonstrates good performance on test data, showing its utility in forecasting diamond prices and understanding market patterns.
+
+Understanding the driving factors of diamond pricing is not only a technical problem, but also an in-depth discussion of the complex dynamics of diamond market.
+The diamond industry is greatly influenced by consumer preferences and changes in market conditions.
+Analyzing and accurately predicting the price based on the intrinsic quality of diamonds (carat weight, color, clarity and cut) is not only meaningful for a single transaction, but also involves a wider range of market and social issues.
+Firstly, the pricing transparency of the diamond market is an important issue.
+Through a reliable pricing model, opacity can be reduced and a fairer price system can be realized.
+This not only protects consumers' rights and interests, but also contributes to the development of market.
+Secondly, studying diamond pricing can help the industry better adapt to the needs of modern consumers.
+By studying the main influencing factors of diamonds, retailers can optimize their inventory and marketing strategies.
+For example, if it is found that the weight of carats has the greatest impact on the price, retailers can give priority to the promotion of diamonds with larger carats, and at the same time highlight this feature in market promotion, so as to meet the needs of consumers more effectively.
+Generally speaking, this study not only provides a more scientific pricing basis for consumers, retailers and appraisers, but also provides guidance for the industry to adapt to dynamic changes.
+
+The remainder of this paper is structured as follows.
+@sec-data discusses data overview, response variable, predictor variables, data measurement and data visualization which includes the plots of each variable and its response, as well as plots of variable interactions.@sec-model shows how to generate the generalized linear regression.
+@sec-result shows the relationship between carat size, color, cut and clarity in diamond price.
+@sec-discussion discusses the results of @sec-result going into detail which shows the complex relationship between sociocultural background and diamond price.
+And it also shows the limitations of research, and proposes the focus that future research should focus on to enhance the depth and accuracy of the research.
 
@@
 Bayesian modeling is conducted with rstanarm [@rstanarm], leveraging robust statistical frameworks.
-Additionally, caTools [@caTools] aids in statistical operations such as ROC curve analysis, and ggcorrplot [@ggcorrplot] facilitates correlation visualization.
+Additionally, caTools [@caTools] aids in statistical operations, and ggcorrplot [@ggcorrplot] facilitates correlation visualization.
 
@@
 
-a. Linear Regression Model:
+a.Linear Regression Model:
 
@@
 
-b. Bayesian regression Model:
+b.Bayesian regression Model:
 
@@
 
-c. Comparision Result:
+c.Comparision Result:
 
@@
 
-## Futurer Direction {#sec-further}
+## Future Direction {#sec-further}
 To improve the depth and reliability of future research, several enhancements to the dataset and model can be considered.
@@
 
-The idealized survey questionnaire can be accessed via the following link:
-
-https://docs.google.com/forms/d/e/1FAIpQLSe9YMFwC4RHHg36c1VY8yA-cZpdrN32yZfeCMJf_jD3qweOQg/viewform?usp=sf_link
-
 ## Survey Questions

### 2024-12-04 paper/paper.qmd
update data measurement

@@
 ---
-title: "my title"
-subtitle: "subtitle"
+title: "Predicting Diamond Pricing: A Generalized Linear Model Analysis"
+subtitle: "Carat Weight Dominates While Cut Plays a Smaller Role in Determining Price"
 author: 
@@
 date-format: long
-abstract: "4 sentence"
+abstract: "This paper investigates how the Four Cs—carat weight, color, clarity, and cut—affect diamond pricing and develops a predictive model using a Generalized Linear Model (GLM) with a Gamma distribution.
+The analysis shows that carat weight has the strongest positive influence on price, followed by clarity and color, while cut has a relatively smaller impact.
+The model demonstrates robust performance, providing a reliable framework for forecasting diamond prices and understanding market patterns.
+These findings enhance pricing transparency, help the diamond industry adapt to shifting consumer preferences, and offer valuable insights into the economic and cultural factors shaping diamond valuation."
 format: pdf
@@
 Additionally, caTools [@caTools] aids in statistical operations, and ggcorrplot [@ggcorrplot] facilitates correlation visualization.
+
+The reason that I chose DASL is its directness and openness of data.
+The data set focuses on the diamond market, contains detailed 4C attributes and prices, directly supports the research objectives, and is completely open, ensuring the repeatability and transparency of the analysis.
+Additionally, there does not exist other data set about diamond price in the data set licensed in @tellingstories.
+However, we can find data about diamond prices from diamond retailers (such as Blue Nile or James Allen).
+However, these data sets usually come from commercial use, so they may have deviations from the inventory or pricing strategies of specific retailers.
+This deviation will limit the universality of the research results in a wider market.
+In addition, there may be some access restrictions to obtain the complete version of these data.
 
@@
 
+Furthermore, @diamonds_data comes from the data crawled by Lou Valente of JMP from the Internet, and is arranged into a form suitable for educational and research purposes.
+This data collection method shows that the data may be collected from publicly available diamond market information or industry-related websites (such as retailer data or industry reports), and then cleaned and structured to ensure that it is suitable for statistical analysis and modeling tasks.
+
 ## Outcome Variable: Price {#sec-outcomevar}
@@
     x = "Index",
-    y = "log(scale(Price)"
+    y = "Price"
   ) +
   theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
+  theme(plot.title = element_text(hjust = 0.5)) +
+  scale_y_continuous(breaks = NULL)
 

### 2024-12-04 paper/paper.qmd
Remove the typo in the paper then upload

@@
 The model demonstrates robust performance, providing a reliable framework for forecasting diamond prices and understanding market patterns.
-These findings enhance pricing transparency, help the diamond industry adapt to shifting consumer preferences, and offer valuable insights into the economic and cultural factors shaping diamond valuation."
+These findings enhance pricing transparency, help the diamond industry adapt to shifting consumer preferences, and provide opinions into the economic and cultural factors shaping diamond valuation."
 format: pdf
@@
 Each of these attributes uniquely influences a diamond's market value.
-Carat size measures the diamond's mass, with larger diamonds being rarer and typically more valuable.
+Carat size measures the diamond's mass, with larger diamonds being rarer and typically more expensive.
 Color grading evaluates the absence of color, ranging from D (colorless) to Z (light yellow or brown), with colorless diamonds commanding higher prices.
@@
 Despite these advancements, there remains a need for analyses diamond price based on other models to enhance the accuracy and reliability of diamond price predictions.
-This research fills this gap by employing a Generalized Linear Model.
+This research employs a Generalized Linear Model to analyze more.
 
@@
 In addition, there are significant outliers in top colors such as D and E, which may be due to the unusually high price of diamonds with large carats or other high-quality characteristics.
-This figure clearly reveals the influence of color grade on price and its market value distribution characteristics.
+This figure clearly shows the influence of color grade on price and its market value distribution characteristics.
 
@@
 
-# 绘制小提琴图
 violin_plot_color <- ggplot(cleaned_data, aes(x = color, y = price)) +
-  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) +  # 添加小提琴图
-  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +  # 在小提琴图中叠加箱线图
+  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
+  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) + 
   labs(
@@
 The scatter chart on the right of @fig-carat_size shows the relationship between the carat size of diamonds and the price.
-It can be clearly seen that the price rises rapidly with the increase of carat size, showing a nonlinear growth trend.
+It can be clearly seen that the price rises quickly with the increase of carat size, showing a nonlinear growth trend.
 Especially in the range of close to 1.0 carats and larger carats, the price increase is more significant.
@@
 
-@fig-correlation_heat shows several key insights about the relationships between diamond attributes and price.
+@fig-correlation_heat shows several key points about the relationships between diamond attributes and price.
 Carat size shows a strong positive correlation with price, indicating that it is one of the primary factors influencing diamond value—larger diamonds tend to be more expensive.
@@
 one_hot_encoded <- cbind(
-  correlated_data %>% select(price, carat_size), # 数值变量
+  correlated_data %>% select(price, carat_size), 
   model.matrix(~ color + clarity + cut - 1, data = correlated_data, 
@@
 \begin{align}
-\log(\mu_i) &= \beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \nonumber \\
-&\quad + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}.
+\log(\mu_i) &= \upsilon_0 + \upsilon_1 x_{1} + \upsilon_2 x_{2}+\upsilon_3 x_{3}+... 
 \end{align}
+
+- $\beta_0$: Intercept term.
+- $\upsilon_i$: Coefficients of predictors.
+- $x_i$: Predictors.
 
@@
 \begin{align}
-\text{price} &= \log(\text{price}) \cdot \sigma + \mu.
+\text{price} &= \log(\text{standardized\ and\ exponentiated\ price}) \cdot \sigma + \mu.
 \end{align}
@@
   geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) +  # Confidence intervals
-  geom_text(aes(label = round(Estimate, 3)), hjust = -0.3, size = 3) +  # Lable estimates
+  geom_text(aes(label = round(Estimate, 2)), hjust = -0.3, size = 3) +  # Lable estimates
   theme_minimal() +  # Minimal theme
@@
 
+To further explain the result of the model, we will show an example of diamond price predictions.
+
+-   Carat size: 1.2
+-   Color: D
+-   Cut: Good
+-   Clarity: VVS2
+
+Based on above features of diamond, we firstly calculate the log(standardized and exponential price). From @fig-modelresults, we can know intercept and the coefficients each variables:
+
+-   Intercpet: -4.81 
+-   carat size: 3.74
+-   color D: 1.34
+-   cut Good: 0, because it is the reference level
+-   clarity VVS2: 0.89
+
+We plog these value into formula (3) and can get the log(standardized and exponential price) is around 1.91.
+Then we will calculate the actual price of the diamond.
+We plog 1.91 into formula (4) and get the price is around 8678.07.
+Therefore, we know a diamond with 1.2 carat size, color D, good cut and VVS2 clarity should be approximately 8678.07 USD.
+
 # Discussion{#sec-discussion}
 
-## Exploration of Model Result {#sec-exploration}
+## Discussion of Model Result {#sec-exploration}
 
@@
 This focus on size shows how people value physical attributes that are easily noticeable, often linking material possessions to social status and personal achievements.
-Economically, the preference for size drives demand for larger diamonds, encouraging industries to focus on producing and marketing them as rare and valuable.
+Economically, the preference for size drives demand for larger diamonds, encouraging industries to focus on producing and marketing them as rare and
+expensive.
 
@@
 
-Although the data set is valuable, there are several limitations, which affect the universality and depth of the research results.
-A key limitation is the limited price range, which only includes diamonds with a price between $1,000 and $10,000.
+Although the data set is good, there are several limitations, which affect the universality and depth of the research results.
+A key limitation is the limited price range, which only includes diamonds with a price between 1,000 USD and 10,000 USD.
 This does not include low-priced and high-end luxury diamonds, which may miss the unique pricing model of these market segments.
@@
 Another limitation is that the data set narrowly focuses on physical properties, such as carat size, color, clarity and cutting, while ignoring background factors such as brand reputation, certification sources and market trends.
-These external factors will significantly affect pricing, but they are not taken into account in the data.
-In addition, the data set lacks geographical and cultural details, which can provide insights into regional differences in preferences and needs.
+These external factors will significantly affect pricing, but they are not considered in the data.
+In addition, the data set lacks geographical and cultural details, which can provide opinions into regional differences in preferences and needs.
 This omission limits the global applicability of the research results, because diamond pricing often varies with the market and consumer base.
@@
 Similarly, the color and clarity variables are not fully represented.
-For instance, diamond color is graded from D (colorless) to Z (light yellow or brown), but the dataset only includes colors from D to K, leaving out lower-grade colors that could provide additional insights.
+For instance, diamond color is graded from D (colorless) to Z (light yellow or brown), but the dataset only includes colors from D to K, leaving out lower-grade colors that could provide additional ideas.
 Moreover, the absence of time-related factors limits the ability to analyze how diamond prices change over time due to shifts in consumer preferences, market trends, or seasonal effects.
@@
 #| fig-cap: "Actual vs Predicted Values"
+
+# Load and deal with the dataset
 test_data <- read_parquet(here("data/02-analysis_data/diamondprice_test_data.parquet"))
-
 test_data$price <- scale(test_data$price, center = TRUE, scale = TRUE)
@@
 
+## Generate predicted prices using the generalized linear model (model_glm)
 test_data$predicted_price <- predict(model_glm, newdata = test_data, type = "response")
 
+# Plot the actual vs. predicted prices
 ggplot(data = test_data, aes(x = 1:nrow(test_data))) +
+  # Add a line for predicted prices
   geom_line(aes(y = predicted_price), color = "lightblue", size = 1, linetype = "solid") +
+  # Add points for actual prices
   geom_point(aes(y = price), color = "palevioletred", size = 2) + 
@@
 This highlights the model's strong ability to provide accurate predictions in most cases and reflects that its performance is not heavily skewed by outliers.
-Compared to MSE, MAE is less sensitive to extreme errors, offering a more balanced perspective on prediction accuracy.
+Compared to MSE, MAE is less sensitive to extreme errors, providing a more balanced perspective on prediction accuracy.
 The RMSE of 1.276, being the square root of MSE, provides a direct measure of the standard deviation of prediction errors in the original data's units.
@@
 
-The "Residuals vs.
-Leverage" plot highlights a few potentially influential points (e.g., 1930, 1899, 1924) with higher leverage.
+The last plot highlights a few potentially influential points (e.g., 1930, 1899, 1924) with higher value.
 Although none of these points exceed Cook’s distance thresholds, their presence warrants closer examination to ensure they do not disproportionately affect the model.
@@
 
+# Set the plotting layout to a 2x2 grid for displaying four plots on one screen
 par(mfrow = c(2, 2))
+
+# Generate diagnostic plots for the generalized linear model (model_glm)
+# 1. Residuals vs Fitted: Checks for patterns in residuals to assess linearity and homoscedasticity
+# 2. Normal Q-Q Plot: Assesses whether residuals follow a normal distribution
+# 3. Scale-Location Plot: Examines homogeneity of variance (spread of residuals)
+# 4. Residuals vs Leverage: Identifies influential data points
 plot(model_glm)
@@
 -   Closed-form questions (multiple choice, Likert scale) to evaluate consumer preferences.
--   Open-ended questions gain insight into the factors affecting prices.
+-   Open-ended questions gain opinions into the factors affecting prices.
 The questionnaire was optimized by small-scale pretest, focusing on reducing the ambiguity of questions and the fatigue of respondents

### 2024-12-04 scripts/00-simulate_data.R
Add comments to 00-simulate_data.

@@ -20,7 +20,7 @@ n <- 141
 
 # Generate simulated data
 simulated_data <- data.frame(
-  price = sample(1000:10000, n, replace = TRUE), # Price range: 1000-10000 as integers
+  price = sample(1000:10000, n, replace = TRUE), # Price range: 1000-10000
   color = sample(c('D', 'E', 'F', 'G', 'H', 'I', 'J', 'K'), n, replace = TRUE), # Color categories
   cut = sample(c('Ideal', 'Good', 'Very Good', 'Excellent'), n, replace = TRUE), # Cut categories
   clarity = sample(c('IF', 'VVS1', 'VVS2', 'VS1', 'VS2', 'SI1', 'SI2'), n, replace = TRUE), # Clarity categories

### 2024-12-04 paper/paper.qmd
Update Ideal Methodology and Ideal Survey

@@
 
+This methodology draws upon existing literature to guide its framework.
+For example, @verbeek2017 points out the importance of stratified sampling and multi-wave data collection in ensuring representative and reliable datasets in market studies.
+Similarly, @syverson2019 emphasizes the role of data standardization and cleaning in enhancing the accuracy of econometric modeling.
+These references underpin the methodological rigor employed in this study, ensuring that it aligns with established best practices in empirical research.
+
 ## SamplingApproach
@@
 
+The survey aims to find consumer behavior, preferences, and perceptions related to diamonds.
+The survey design incorporates both structured and open-ended questions to balance quantitative rigor with qualitative ideas.
+Questions address demographic characteristics, behavioral patterns, perceptions of diamond characteristics, and satisfaction with previous purchases.
+
+This survey design is informed by prior research.
+For example, @dhaliwal2020 analyzes the importance of open-ended questions in uncovering consumer preferences in the luxury market.
+In addition, @wilson2018 recommend a mix of Likert-scale and multiple-choice questions to enhance respondent engagement and reduce fatigue.
+These studies guide the development of a good questionnaire that maximizes data quality while ensuring respondent satisfaction.
+
 ## Survey Questions

### 2024-12-08 paper/paper.qmd
Update bibliography

@@
 bibliography: 
-  - references .bib
+  - references.bib
 toc: true

### 2024-12-14 scripts/01-test_simulated_data.R
Add more methods to test simulated data

@@ -75,3 +75,40 @@ if (all(!is.na(simulated_data))) {
 } else {
   stop("Test Failed: The dataset contains missing values.")
 }
+
+
+# Check if 'price' is numeric
+if (is.numeric(simulated_data$price)) {
+  message("Test Passed: 'price' column is numeric.")
+} else {
+  stop("Test Failed: 'price' column is not numeric.")
+}
+
+# Check if 'color' is character
+if (is.character(simulated_data$color)) {
+  message("Test Passed: 'color' column is character.")
+} else {
+  stop("Test Failed: 'color' column is not character.")
+}
+
+# Check if 'cut' is character
+if (is.character(simulated_data$cut)) {
+  message("Test Passed: 'cut' column is character.")
+} else {
+  stop("Test Failed: 'cut' column is not character.")
+}
+
+# Check if 'clarity' is character
+if (is.character(simulated_data$clarity)) {
+  message("Test Passed: 'clarity' column is character.")
+} else {
+  stop("Test Failed: 'clarity' column is not character.")
+}
+
+# Check if 'carat_size' is numeric
+if (is.numeric(simulated_data$carat_size)) {
+  message("Test Passed: 'carat_size' column is numeric.")
+} else {
+  stop("Test Failed: 'carat_size' column is not numeric.")
+}
+

### 2024-12-14 paper/paper.qmd
update the captions of graphs

@@
 
-We use the statistical programming language R [@citeR], alongside several key libraries and datasets to analyze and visualize data effectively.
+We use the statistical programming language R [@citeR], alongside several key libraries and data sets to analyze and visualize data effectively.
 Our data [@diamonds_data] is sourced from the Data and Story Library, providing detailed attributes of diamonds for multiple regression analysis.
@@
 The reason that I chose DASL is its directness and openness of data.
-The data set focuses on the diamond market, contains detailed 4C attributes and prices, directly supports the research objectives, and is completely open, ensuring the repeatability and transparency of the analysis.
+The data set focuses on the diamond market, contains detailed 4C attributes and prices, directly supports the research objectives, and is completely open, ensuring the reproducibility and transparency of the analysis.
 Additionally, there does not exist other data set about diamond price in the data set licensed in @tellingstories.
@@
 The diamond price is a continuous numerical variable, ranging from close to 1000 USD to 10,000 USD.
-Through the histogram of @fig-price, we can find that the price of diamonds has obvious right skewness, and with the increase of price, the number of diamonds decreases gradually.
-In addition, combining the histogram and box chart in @fig-price, we can find that there is no obvious abnormal value of diamond prices.
+Through the left graph of @fig-price, we can find that the price of diamonds has obvious right skewness, and with the increase of price, the number of diamonds decreases gradually.
+In addition, in @fig-price, we can find that there is no obvious abnormal value of diamond prices.
 Most diamond prices are concentrated in the range of 2,500 USD to 5,000 USD, with an average price of about 4,000 USD and a median of 3,500 USD, indicating that a few high-priced diamonds have raised the overall average.
@@
 
-The barplot on the left of @fig-color shows the distribution of diamond color from D to K.
-The barplot shows that the number of diamonds with color grades E and F is the largest, indicating that these nearly colorless diamonds are more popular in the market, probably because they have high quality and cost performance.
+The left graph of @fig-color shows the distribution of diamond color from D to K.
+It shows that the number of diamonds with color grades E and F is the largest, indicating that these nearly colorless diamonds are more popular in the market, probably because they have high quality and cost performance.
 In contrast, the number of completely colorless D-class diamonds and K-class diamonds with slight yellow is small, which may be due to their rarity and color deviation, respectively, resulting in low demand.
 This picture directly reflects the supply of diamonds of different color grades in the market and their potential demand trends.
-The violin chart on the right of @fig-color shows the distribution of diamond prices in different color grades.
-The violio chart shows that the prices of diamonds with color grades D to F are generally higher, especially those with color grades D and E, which shows a wider price distribution range, indicating that the prices of high-end diamonds with these color grades can increase significantly.
+The right graph of @fig-color shows the distribution of diamond prices in different color grades.
+It shows that the prices of diamonds with color grades D to F are generally higher, especially those with color grades D and E, which shows a wider price distribution range, indicating that the prices of high-end diamonds with these color grades can increase significantly.
 In contrast, the price distribution of diamonds with color grades I to K is more concentrated and the overall price is lower, reflecting that the price fluctuation of diamonds close to yellow is less in the market.
 In addition, there are significant outliers in top colors such as D and E, which may be due to the unusually high price of diamonds with large carats or other high-quality characteristics.
-This figure clearly shows the influence of color grade on price and its market value distribution characteristics.
+It clearly shows the influence of color grade on price and its market value distribution characteristics.
 
@@
   theme_minimal() +
-  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))
+  theme(plot.title = element_text(size = 10, face = "bold",hjust = 0.5 ))
 
@@
   labs(
-    title = "Violin Plot of Price by Color",
+    title = "Price Distribution\nAcross Diamond Colors",
     x = "Diamond Color",
@@
   theme_minimal()+
-  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))
+  theme(plot.title = element_text(size = 10, face = "bold",hjust = 0.5 ))
 
@@
 
-The diamond carat size, a continuous numerical variable representing the weight of the diamond, ranges from approximately 0.30 to 2.02 carats in the dataset.
+The diamond carat size, a continuous numerical variable representing the weight of the diamond, ranges from approximately 0.30 to 2.02 carats in the data set.
 One carat is equivalent to 200 milligrams, making it a key factor in determining the diamond's size and price.
-The histogram on the left of @fig-carat_size shows the distribution of the Carat Size of diamonds.
+The left graph of @fig-carat_size shows the distribution of the Carat Size of diamonds.
 On the whole, it presents a right-skewed distribution, indicating that the number of small carats (such as 0.5 to 1.0 carats) is the largest in the market, while the number of larger carats is gradually decreasing.
@@
 This reflects that consumers have higher demand for small carats, while large carats are scarce because of their rarity and high price.
-The scatter chart on the right of @fig-carat_size shows the relationship between the carat size of diamonds and the price.
+The right graph of @fig-carat_size shows the relationship between the carat size of diamonds and the price.
 It can be clearly seen that the price rises quickly with the increase of carat size, showing a nonlinear growth trend.
 Especially in the range of close to 1.0 carats and larger carats, the price increase is more significant.
-This shows that the carat size has an important influence on the diamond price, but when the Dancla size exceeds a certain value (such as 1.5 carats), the price growth rate tends to be flat.
+This shows that the carat size has an important influence on the diamond price, but when the Diamond size exceeds a certain value (such as 1.5 carats), the price growth rate tends to be flat.
 In addition, the fitted black curve further clearly shows this nonlinear relationship, indicating that the marginal effect of carat size on price decreases.
@@
   theme_minimal()+
-  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))
+  theme(plot.title = element_text(size = 10, face = "bold",hjust = 0.5))
 
@@
 
-The barplot on the left of @fig-clarity shows the distribution of diamond Clarity.
+The left graph of @fig-clarity shows the distribution of diamond Clarity.
 It shows that the number of diamonds with clarity grades SI1 and SI2 is the largest, indicating that these grades of diamonds are the most widely available in the market, probably because they have higher cost performance and greater market demand.
@@
 This shows that diamonds with lower definition grades (such as SI1 and SI2) are the main ones in the market, while high definition diamonds are scarce.
-The violin chart on the right of @fig-clarity shows the distribution of diamond prices at different clarity levels.
+The right graph of @fig-clarity shows the distribution of diamond prices at different clarity levels.
 With the improvement of clarity, the price rises significantly, especially for diamonds with high definition such as IF and VVS1.
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
-  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))
+  theme(plot.title = element_text(size = 10, face = "bold",hjust = 0.5))
 
@@
   labs(
-    title = "Violin Plot of Price by Clarity",
+    title = "Price Distribution\nAcross Diamond Clarity",
     x = "Clarity",
@@
 
-The barplot on the left of @fig-cut shows the distribution of diamonds with different cutting grades.
+The left graph of @fig-cut shows the distribution of diamonds with different cutting grades.
 It indicates that the number of diamonds with Excellent and Very Good grades is obviously more, indicating that most diamonds on the market are concentrated in these high-cut grades, which may be because they have better visual effects and higher market demand.
 In contrast, the number of Good and Ideal diamonds is small, especially the rarity of Ideal cutting may reflect strict cutting ratio requirements and high quality standards.
-The violin chart on the right of @fig-cut shows the price distribution of diamonds with different cutting grades.
+The right graph of @fig-cut shows the price distribution of diamonds with different cutting grades.
 It shows the price range of each cutting grade is very close to the median, which shows that the cutting grade has little direct influence on the price.
@@
   labs(
-    title = "Violin Plot of Price by Cut",
+    title = "Price Distribution\nAcross Diamond Cut",
     x = "Diamond Cut",
@@
 #| label: fig-correlation_heat
-#| fig-cap: "Correlation: Heat Graph"
+#| fig-cap: "Correlation Matrix of Diamond Attributes"
 
@@
 
-Despite its advantages, the GLM has potential limitations and may not be suitable in certain scenarios.
-When the distribution of response variable is hard to observe, we may not able to assume its distribution.
+While GLM has advantages, it may face limitations when response variable distributions are unclear.
 Furthermore, highly nonlinear relationships may not be adequately captured by the specified link function, requiring alternative modeling approaches.
@@
 The variability of the transformed prices increases at higher indices, but the model does not fully capture this.
-This suggests that the GLM model, with its fixed Gamma distribution and log link function, may oversimplify the behavior of the response variable in these regions.
-The underestimation at higher levels highlights potential limitations in the model’s assumptions.
+This suggests that the GLM model’s fixed Gamma distribution and log link may oversimplify response variable behavior, leading to underestimation in higher price ranges.
 

### 2024-12-15 paper/paper.qmd
remove banned words/phrases

@@
 
-The dataset also simplifies some predictor variables, particularly cut quality, by classifying them into broad groups (Ideal, Excellent, Very Good, and Good) without accounting for finer details like proportions or symmetry.
-These details, such as the arrangement of facets or crown angles, are crucial for evaluating a diamond's brilliance and could provide a deeper explanation for price variations.
+The data set also simplifies some predictor variables, particularly cut quality, by classifying them into broad groups (Ideal, Excellent, Very Good, and Good) without accounting for finer details like proportions or symmetry.
+These details, such as the arrangement of facets or crown angles, are important for evaluating a diamond's brilliance and could provide a deeper explanation for price variations.
 Similarly, the color and clarity variables are not fully represented.
-For instance, diamond color is graded from D (colorless) to Z (light yellow or brown), but the dataset only includes colors from D to K, leaving out lower-grade colors that could provide additional ideas.
+For instance, diamond color is graded from D (colorless) to Z (light yellow or brown), but the data set only includes colors from D to K, leaving out lower-grade colors that could provide additional ideas.
 Moreover, the absence of time-related factors limits the ability to analyze how diamond prices change over time due to shifts in consumer preferences, market trends, or seasonal effects.
@@
 While RMSE tends to be slightly higher than MAE because it gives more weight to larger errors, its relatively low value confirms the model's stability and reliable performance on the test data.
-However, the gap between RMSE and MAE suggests the presence of some larger errors or outliers that may require further investigation.Overall, these metrics indicate that the GLM performs well in predicting diamond prices, with reasonable accuracy and controlled error levels.
+However, the difference between RMSE and MAE suggests the presence of some larger errors or outliers that may require further investigation.Overall, these metrics indicate that the GLM performs well in predicting diamond prices, with reasonable accuracy and controlled error levels.
 
@@
 
-## SamplingApproach
+## Sampling Approach
 
